---
title: "The Effect of Fraternity Moratoriums on Alcohol Offenses and Sexual Assaults"
author: Michael Topper^[PhD Candidate in the Economics Department at the University
  of California, Santa Barbara (michaeltopper@ucsb.edu). I would like to thank Heather
  Royer, Kevin Schnepel, Dick Startz, Kelly Bedard, Clément de Chaisemartin, Toshio
  Ferrazares, Anna Jaskiewicz, Elizabeth Tucker, and the members of the UCSB 290 Applied
  Research Group for their advice and feedback on various drafts of this paper. Special
  thanks to Terry Cheng, all public records officials, Fraternity and Sorority Life
  advisors, and police department officials who assisted me in collecting the data
  used in this paper. All errors are my own. \vspace{\baselineskip}]
subtitle: ''
output:
  pdf_document:
    number_sections: yes
    extra_dependencies: flafter
indent: yes
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage{bbm}
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage{indentfirst}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\doublespacing
- \usepackage{subfig}
- \usepackage{placeins}
- \usepackage{rotating}
- \usepackage{fancyhdr}
- \usepackage{times}
- \usepackage{endnotes}
- \floatplacement{figure}{H}
linkcolor: blue
bibliography: references.bib
link-citations: yes
nocite: "@cameron_bootstrap-based_2008\n"
abstract: "\\singlespacing I exploit variation in timing from 44 temporary university-wide
  halts on all fraternity activity with alcohol (*moratoriums*) across 37 universities
  over 2014-2019. I construct a novel data set, merging incident-level crime logs
  from university police departments to provide the first causal estimates of the
  effect of moratoriums on reports of alcohol offenses and sexual assaults. In particular,
  I find robust evidence that moratoriums decrease alcohol offenses by 26%. Additionally,
  I find suggestive evidence that moratoriums decrease reports of sexual assault on
  the weekends by 29%. However, I do not find evidence of long-term changes once the
  moratorium is lifted."
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(kableExtra)
library(bookdown)
library(modelsummary)
library(fixest)
library(grid)
library(gridExtra)
library(patchwork)
options(modelsummary_model_labels="model")
```

<center>
\singlespacing
\thispagestyle{empty}
\noindent \textbf{JEL Codes:} I12, I28, K42 \vspace{\baselineskip}

\noindent Please note that an Online Appendix is included. \vspace{\baselineskip}

\noindent \textbf{Disclosure Statement:} I, Michael Topper, declare that I have no relevant or material financial interests that relate to the research described in this paper. \vspace{\baselineskip}

\noindent \textbf{Data Replication Statement:}  This paper uses a combination of publicly available data from multiple sources. The raw data can be obtained through Clery Act/Freedom of Information requests at each unique university. Additionally, I am willing to assist in data requests for replication (michaeltopper@ucsb.edu). All replication files, including the master data, are available at github.com/michaeltopper1/Fraternities. 


</center>
```{=tex}
\renewcommand{\thesubsection}{\Alph{subsection}} 
```


\newpage
```{=tex}
\doublespacing
\let\oldfootnote\footnote % Save the original definition of \footnote
\let\footnote\endnote % Redefine \footnote to \endnote
```

\pagenumbering{arabic}
```{r, child = "paper_iterations/accepted_paper/introduction.Rmd"}

```

```{r, child="paper_iterations/accepted_paper/data.Rmd"}

```

```{r, child="paper_iterations/accepted_paper/empirical_strategy.Rmd"}

```

```{r, child = "paper_iterations/accepted_paper/results.Rmd"}

```

```{r, child = "paper_iterations/accepted_paper/heterogeneity.Rmd"}

```

```{r, child = "paper_iterations/accepted_paper/conclusion.Rmd"}

```

\newpage
# References

<div id="refs"></div>

\newpage
\FloatBarrier
\theendnotes


\newpage
```{=tex}
\let\footnote\oldfootnote % Restore the original definition of \footnote
```

```{r, child = "paper_iterations/accepted_paper/tables.Rmd", fig.pos = "H", cache=TRUE}

```

\newpage
```{r, child = "paper_iterations/accepted_paper/figures.Rmd", fig.pos="H", cache=TRUE}

```

\newpage


```{=tex}
\FloatBarrier
\vspace{1in}
\begin{center}
{\LARGE The Effect of Fraternity Moratoriums on Alcohol Offenses and Sexual Assaults}\\
{Michael Topper} \\
\vspace{2in}
{\LARGE \textbf{Online Appendix}}\\
\thispagestyle{empty}
\end{center}
```

\newpage
```{=tex}
\appendix
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{A\arabic{table}} \setcounter{equation}{0}
\setcounter{footnote}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/accepted_paper/appendix_data.Rmd", fig.pos='H' }

```

\newpage

```{=tex}

\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{B\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/accepted_paper/appendix_twfe.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{C\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/accepted_paper/appendix_spillover.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{D\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/accepted_paper/appendix_fraction_ifc.Rmd", fig.pos='H' }

```




\newpage
```{=tex}
\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{E\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```
```{r, child = "paper_iterations/accepted_paper/appendix_figures.Rmd", fig.pos='H', cache=TRUE }

```

