---
title: "other stuff I may need"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# From lit review

**Drop from here**

@ferman_synthetic_2019 investigate the validity of synthetic control when the pretreatment fit is imperfect. They show the synthetic control estimator is biased if the treatment assignment is correlated with unobserved confounders regardless of pretreatment size. The authors then suggest modified versions of the estimator to greatly reduce the bias.

**To here**



\newpage 

The four models are abbreviated in the following plots:

**BL TVP**: Bayesian Lasso Time Varying Parameter (green)

**BL No TVP**: Bayesian Lasso No Time Varying Parameter (red)

**CI No TVP**: Causal Impact No Time Varying Parameter (blue)

**CI TVP**: Causal Impact Time Varying Parameter (pink)

\newpage

```{r, out.width = "50%", fig.cap = "Example Plots Constant Coefficients 0 Treatment Effect", fig.show="hold", fig.ncol=2, fig.align="center"}
knitr::include_graphics("../04-sim/simulation_res_bl/stab_0lift_plot.pdf")
```

\newpage

```{r, out.width = "50%", fig.cap = "Example Plots Constant Coefficients 5 Treatment Effect", fig.show="hold", fig.ncol=2, fig.align="center"}
knitr::include_graphics("../04-sim/simulation_res_bl/stab_5lift_plot.pdf")
```

\newpage

```{r, out.width = "50%", fig.cap = "Example Plots Deterministic Continuous Varying Coefficients 0 Treatment Effect", fig.show="hold", fig.ncol=2, fig.align="center"}
knitr::include_graphics("../04-sim/simulation_res_bl/tvp_0lift_plot.pdf")
```

```{r, out.width = "50%", fig.cap = "Example Plots Deterministic Continuous Varying Coefficients 5 Treatment Effect", fig.show="hold", fig.ncol=2, fig.align="center"}
knitr::include_graphics("../04-sim/simulation_res_bl/tvp_5lift_plot.pdf")
```

