---
title: "Fraternities and Sexual Assault"
subtitle: ""
author: 
  - Michael Topper
date: "Last Updated: `r Sys.Date()`"
output: 
  pdf_document:
    number_sections: true
    # latex_engine: xelatex # If i hashtag it out my code works? I'm not sure
indent: true
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage{indentfirst}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\doublespacing
- \usepackage{subfig}
- \theoremstyle{definition}
- \newtheorem{definition}{Definition}[section]
- \newtheorem{assumption}{Assumption}
- \newtheorem{theorem}{Theorem}[section]
- \newtheorem{corollary}{Corollary}[theorem]
- \newtheorem{lemma}[theorem]{Lemma}
- \newtheorem*{remark}{Remark}
- \newcommand{\magenta}[1]{\textcolor{magenta}{#1}}
- \newcommand{\indep}{\perp \!\!\! \perp}
- \floatplacement{figure}{H}
- \bibliographystyle{plainnat}
bibliography: "references.bib"
link-citations: yes
linkcolor: blue
abstract: This is to be completed later when I have all of the final covarites.
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(bookdown)
library(readr)
library(tidyverse)
library(dplyr)
```



\section{Introduction}
  (*This section is the only section has not been updated since last 290 meeting. All other sections have been updated*) Rape remains prevalent on all university campuses. According to the Campus Climate Survey on Sexual Assault and Sexual Misconduct conducted by the Association of American Universities, the overall rate of nonconsensual sexual contact since a student enrolled at their respective college was 13% in 2019.^[This number comes from the 33 large universities that participated in the survey.] Additionally, this percentage has increased since 2015^[Of the 21 schools that participated in both the 2015 and the 2019 surveys, results showed a 3% increase for undergraduate women, 2.4% increase for graduate and professional women.] with the largest increases stemming from undergraduate women. Academics have pointed to multiple sources of this heinous behavior including college partying with alcohol [@lindo_college_2018], liquor violations [@wiersma-mosley_empirical_2017], and most pertinent, fraternities [@foubert_behavior_2008]. In the book *Sexual Assault on Campus: The Problem and the Solution*, the authors Carol Bohmer and Andrea Parrot claim that “the men who are most likely to rape in college are fraternity pledges.”^[A fraternity pledge is another name for a first-year member of a fraternity.] Furthermore, academic studies using survey data have found that fraternity men were more likely to commit sexual assault than men who did not join a fraternity [@foubert_behavior_2008], university males rated sexual assault perpetrators as less guilty when the perpetrator was a fraternity member [@seabrook_bros_2019], and sorority women (who interact with fraternity men frequently) were sexually assaulted at four times the rate of non-sorority women [@minow_sorority_2009]. Universities have responded to fraternity-related misconduct with a range of policy initiatives, and in particular, placing moratoriums on fraternity social-life. Each of these moratoriums occurs campus-wide, thereby affecting all fraternities simultaneously. And while the moratorium guidelines vary by university, each of them prohibits fraternity social gatherings with alcohol. This paper exploits the variation in timing of 39 fraternity moratoriums at 34 four-year universities across the US to estimate a causal effect of fraternity moratoriums on cases of rape. 

\section{Background: Fraternities in the US}
In the context of universities, a fraternity is a group of men who gather for social, academic, or demographic interests. Fraternities are a ubiquitous presence at many four-year universities.^[To my knowledge, IFC fraternities do not exist officially at any community colleges or trade schools.] In 2015, the North American Interfraternity (NIC) conference noted that there were over 5500 chapters (groups) located on over 800 campuses in the US and Canada.  According to the US News Reports, some universities have fraternity membership as high as 85%. The overall composition of fraternity members tend to  have family income and education higher than non-members [@routon_impact_2014], while economic studies have linked fraternity membership to higher academic performance [@cheng_greek_2018], alcohol consumption [@routon_impact_2014], and future income [@mara_social_2018]. However, this study, to my knowledge, is the first to estimate the effect of fraternity moratoriums in any context. 

This analysis focuses on a subset of fraternities known as the Interfraternity Council (IFC). These fraternities are composed of individual chapters that are “social fraternities,” although their values are far more outreaching than this. According to their website, the IFC “exist to promote the shared interests and values of our member fraternities: leadership service, brotherhood, and scholarship.”  

To become a member of an IFC fraternity, prospective members must apply (“pledge”) during recruitment events that take place at least once a year. Once a chapter and prospective member jointly accept membership, the new member must abide by the chapter’s guidelines. Figure \ref{fig:sigmaalpha} shows an example of the overarching rules within the chapter, Sigma Alpha Epsilon--one of the oldest fraternity chapters across the US. Each member must maintain a GPA over a certain threshold, pay an initiation and semesterly fee, attend chapter ritual events and meetings, be involved in one additional campus or community organization, and complete service hours. Upon membership, pledges are invited to live within the fraternity house^[Not all fraternities have houses where their members live. While I certainly need to verify this, I am confident that all schools in the sample have fraternity houses on, or near, campus.], although national statistics for what percentage of pledges take this offer are not available. 

Each chapter house has its unique set of rules and atmosphere. In one field study, students at universities were surveyed about their opinions at each chapter house on campus. In the perceived “high risk” houses, social behavior differed dramatically from “low risk” houses—high risk house parties had skewed gender ratios, more segregation between men and women, and men engaged in more jokes and conversations that degraded women than low risk houses [@boswell_fraternities_1996]. However, all fraternities interact with sorority chapters frequently, whose members have been found to consume alcohol with greater frequency, delay assessments of threat, and have significantly higher rates of drugging victimization than non-sorority members ([@franklin_sorority_2016],[@lasky_binge_2017]). Moreover, each chapter is overseen by three sources of jurisdiction: the IFC, the university^[A chapter must be recognized by the university to be under its jurisdiction. This involves following the guidelines administered by the university on social activities and behavior.], and the chapter's national headquarters. Each of these entities has the power to restrict fraternity behavior, although only the IFC and university can implement a campus-wide moratorium. While study only focuses on campus-wide moratoriums, it is important to note that individual chapter moratoriums occur frequently each year. 

\section{Fraternity Moratoriums}
The sample consists of 43 campus-wide moratoriums occurring across the US (Figure \ref{map}). Table \ref{tab:closuretable} shows the universities in the sample and their corresponding moratorium dates and lengths. The average length of the moratoriums was 70 days and the majority of universities (88%) only experienced one moratorium in the sample period. Importantly, each moratorium differs substantially across universities in terms of triggering event (i.e. the event that resulted in the moratorium), restrictions, and governing body that oversaw the moratorium. Figure \ref{triggerevent} shows the distribution of triggering events by the governing body that enacted it. Sexual assault reports and hazing allegations account for 20% of campus moratoriums, while deaths and racist activity account for 15 and 5 percent respectively. Alcohol violations, re-evaluation due to national trends, and unspecified rule violations are grouped into their own category (“Other”) with consisting of the remaining 41%. University and IFC implemented moratoriums are evenly balanced on their triggering events outside of deaths and racist activity where universities possess the entire density. 

\section{Data}
The main analysis uses data from the Uniform Crime Reporting (UCR) Program from the FBI. The UCR systematically collects crime data from local police departments and aggregates them to the agency-month level. In particular, it contains information on the total number of rape incidences reported by each department. Each local police department and university-specific police agency was connected to a corresponding university area using the most recent Law Enforcement Agency Identifiers Crosswalk^[To match law enforcement agencies with schools, the data was filtered by local police agencies and four-year university police departments. Each university police department has a “place code” which is an area that that particular police department covers. However, there are other police departments in these areas that also serve universities, and each of these was attached to the school, although some that were obviously not serving the university (e.g. nearby community college police) were withdrawn.] (LEAIC). Since the crosswalk is not updated yearly, I only observe the population that the local police department serves for one year. Table \ref{tab:orischools} shows the universities and their corresponding local municipalities that serve them. On average, there are approximately two law enforcement agencies that serve each university area--a dedicated university police and a more encompassing local municipality. Notably, reports of rape are significantly lower for university police departments than the local municipalities. Figure \ref{boxplot} illustrates this discrepancy by plotting the distribution of per-capita reports of rape of university-police and local municipalities. Per-capita rape is defined in the sample as the total reports of rape divided by the population each police department serves. For example, if a police department serves a local community/city, I use the population number provided in the LEAIC. On the other hand, if the police department is university specific, I divide the reports of rape within this department by the total enrollment of the university. 

The sample, which consists of 38 unique 4-year degree-granting universities, begins in 2013 to correspond with the year the UCR changed its definition of rape to include non-consenting acts from both males and females in addition to acts of oral or anal penetration. Due to this change, I limit my sample to all media-known,^[The schools that I observe in my sample all had some form of media article or press release from a school /local newspaper. While these may not be the universe of campus-wide moratoriums, they are, to my knowledge, the only events that received media attention.] campus-wide moratoriums of fraternity life from the years 2013-2018.^[My preferred sample will include 2019 when the UCR is updated.] Each campus-wide moratorium was collected through three methods: a time-specific Google search using key phrases,^[Some (although certainly not all) of the searches I used include "fraternity moratorium", "all fraternity closed", "all fraternity suspended", "all fraternities suspended", and "Greek life closure".] a private Facebook group for fraternity and sorority life directors/affiliates to post related articles, and discussions with board members of the Association of Fraternity/sorority Advisors (AFA) and university fraternity and sorority life staff. Each moratorium's date has been verified by either a news article or an email/phone conversation with the corresponding university staff.

Of the 38 universities included, 89% are public, and 13% have appeared at least once in the Princeton Review Top Party Schools list in the corresponding time frame. Table \ref{tab:summarystats} shows descriptive statistics of the universities from the Integrated Postsecondary Education Data System (IPEDS) and the corresponding average reports of rape. The average monthly report of rape is approximately 4 with a large standard deviation of 7. The average undergraduate enrollment is roughly twenty-two thousand, although the standard deviation is large at over twelve thousand. Graduation rates vary significantly across the schools, as the maximum graduation rate reaches over ninety percent, while the minimum is approximately forty two percent. On average, the universities are composed primarily of white individuals (~60%). There is a wide range of college selectivity with average SAT 75th percentiles ranging from nearly perfect scores (790/800) to relatively average scores (528/800). 

*It is important to note that at this time, the data is not entirely complete. I am currently in the process of collecting semesterly hazing reports, chapter numbers, IFC population, fraternity and sorority life population, pledge population, and by-day campus crime reports through Freedom of Information Act (FOIA) requests to enrich the data. *

\section{Empirical Strategy}
I estimate the effects of campus-wide fraternity moratoriums on reports of rape using the variation in the timing of the implementation dates. In particular, I estimate the following model:
\begin{equation}\label{model}
	PercapitaRape_{u,t,a} = \alpha_a + \rho_u  + \phi_t + \beta_{fe} Moratorium_{u,t,a} + \gamma Moratorium_{u,t,a} \times Uni_{u,t,a} +  \mathbb{X}_{u,t,a} + \epsilon_{u,t,a}
	\end{equation}
\noindent where $PercapitaRape_{u,t}$ is the count of reported rapes in police agency $a$, at university $u$, in time $t$. Since treatment lengths vary in time across months, $Moratorium_{u,t,a}$ is a continuous variable between 0 and 1 that represents the proportion of moratorium days in each month. For instance, Texas State University experienced a moratorium on 11/14/2017 that ended on 2/26/2018. In this case, $Moratorium_{u,t,a}$ would be equal to `r round(16/30,2)`  in the month of November ((30-14)/30), 1 in the months of December and January (31/31), and `r round(26/28,2)` in February (26/28). This allows for a measure of treatment intensity, as a month with a small proportion of days that are treated differs from a month that is completely treated. $\mathbb{X}_{u,t,a}$ is a vector of covariates including graduation rate, full-time enrollment, university selectivity, and undergraduate population/demographics corresponding to each university $u$ or agency $a$ at time $t$. However, the critical covariates of fraternity membership and pledge populations by semester are still incomplete and will be added in future iterations. The inclusion of university ($\rho_u$), police agency ($\alpha_a$) and month-by-year fixed effects ($\phi_t$) controls for any time-invariant differences between universities, police agencies, and time of year. This is crucial, as universities differ in social cultures, and reports of sexual assault change seasonally [@mclean_climatic_2007]. Finally, $Uni_{u,t,a}$ is an indicator variable equal to 1 if a university enacted the moratorium, rather than the IFC. Therefore, $\gamma$ would represent the difference between university and IFC implemented moratoriums on reports rape.

Additionally, I estimate a model similar to Equation \ref{model}, but interchange the outcome variable to $Log(Rape_{u,t,a} + (Rape_{i,t}^2 + 1)^{\frac{1}{2}})$. This outcome variable is the inverse-hyperbolic-sine (IHS) transformation of the number of reported rapes at university $u$ at agency $a$ in time period $t$. This transformation is preferred to the natural-log transformation as it is defined at 0 (57% of my rape data is recorded as 0) and it reduces the influence of extreme values in the outcome variable [@burbidge_alternative_1988].

The model’s identifying assumption is that universities that have, or will, experience a moratorium are a good counterfactual for universities undergoing a moratorium conditional on the covariates mentioned above. Additionally, there are several other assumptions needed to estimate causal effects: no anticipation, common trends, and no change in reporting of rapes. 

\subsection{No Anticipation}
To obtain causal estimates, fraternity moratoriums must not be anticipated. As Figure \ref{triggerevent} shows, 15% were due to a fraternity death and 5% were because of racist activity. These events are plausibly unexpected, although they only account for 20% of the moratoriums. However, the other 80% (hazing, sexual assault, alcohol violations, rule violations) are consequences that could lead chapters to anticipate their own house being suspended, but these events are unlikely to lead fraternity members to believe that their entire community will face a moratorium. 

\subsection{Common Trends}
To support the common trends assumption, I estimate an event study model with the following specification:
\begin{equation}\label{eventstudymodel}
Y_{u,t,a} = \alpha_a + \rho_u  + \phi_t + \sum_{t=-8, t\neq -1}^{t = 2}\beta_{t}\mathbb{I}(Moratorium_{u,t,a})  + \epsilon_{u,t,a}
\end{equation}
\noindent where $Y_{u,t,a}$ is either per-capita or IHS transformation of reports of rape. I include all universities with completed moratorium begin and end dates except University of Central Florida, which has only 2 months of pre-trends (refer to Feedback section for question). The end points are binned so the dummy for the final lag and lead are equal to 1 for times $(-\infty, -8]$ and $[2,\infty)$ respectively. I omit the month before the beginning of a moratorium for my reference period, and hence, all coefficients are relative to the month-before moratorium. I show only 2 months following a fraternity moratorium so that the entire sample, excluding University of Central Florida, could be added to the graph. 

Figure \ref{eventstudy} shows the event study trends of rape reports before and after the moratoriums. In the months leading to a moratorium, the means oscillate around zero in a non-systematic fashion with the confidence intervals containing zero. 

\subsection{Changes in Reports of Rape}
The sample only observes reported rapes which has been estimated to be 12% of the true occurrences for students (Kilpatrick 2007). Therefore, it is imperative to test that the likelihood of reporting a rape is not changing because of a campus-wide moratorium on fraternities. If reports of rape are systematically underreporting during of a fraternity moratorium (e.g. fear of blame) then the model would be underestimating the true effect. On the other hand, if reports of rape are systematically overreporting concurrently with a moratorium period (e.g. more victims come forward because fraternities are under more pressure), than the model would be overestimating the results. As an indirect test of whether reports of rape are changing due to moratoriums, I estimate Equation \ref{model} on the number of rapes cleared. A cleared offense, as defined by the UCR, is an offense that has ended in arrest or "by exceptional means". The latter refers to whether the police agency was able to identify the offender, gather enough evidence to support an arrest, identify the offender's exact location, or encountered a circumstance outside the control of law enforcement that prohibits the agency from arresting, charging, or prosecuting the offender. Table \ref{tab:cleared} shows that moratoriums have no significant effect on a report of rape being cleared. Column 1 shows the estimation with no controls, but with added university-by-year fixed effects. Column 2 shows my preferred specification including controls without university-by-year fixed effects. In each of these specifications, there is no significant effect on the types of rapes being cleared.

\section{Preliminary Results}

 *Please note that these results are very preliminary. I have not written this up formally, and am still trying to understand which model I want to use, and which controls. I decided to show some results I find interesting, but a little confusing.* 

Preliminary results are shown in Table \ref{tab:regression} and \ref{tab:regression2}. Note that these results are excluding three schools that do not yet have confirmed moratorium end dates. I differentiate the results between all of the police municipalities, and only the university police departments. Column one shows a regression specification featuring no controls outside of an interaction term between a university enacted moratorium and a moratorium. This interaction term shows the difference between the moratorium effects between a university enacted moratorium in comparison to an IFC-enacted moratorium. Interestingly, university enacted moratoriums have a smaller effect on reports of rape compared to a IFC-enacted moratorium, although this is not statistically significant. Column one's specification also includes month-by-year, agency, and university-by-year fixed effects. I included the university-by-year fixed effects in this first specification as an alternative method of using control variables since all of the university-characteristic data is at the yearly level. Columns 2, 3, and 4 relate to my main specification as shown in Equation \ref{model}, however, I remove and add-in a few control variables that have been causing some confusion. In particular, the "Proportion Foreign," or the proportion of international students, drastically changes my results from an insignificant negative effect, to a very strong negative effect while shrinking my standard errors.

At this time, I am still unsure which model specification I want to use. Each contain similar results, but the per-capita outcome variable is easier to explain while the IHS is easier to read.  Since vital control variables are still missing (fraternity population and new member population by school), these results are not final. Without the control variables of fraternity/new member population by university, I am not comparing schools that have similar prevalence of fraternity activity. 


\section{Feedback Wanted}

* I need to figure out a sample and stick with it. I know that all of my regressions are taking observations in and out. This is being caused by the covariates "SAT score" and "proportion foreign". How important are these variables? In my opinion, SAT score gives a level of selectively in schools, and behavior across selectively could be crucial. Moreover, schools with higher proportion of international students may have differences in student behavior. 

* I think I need to stick with 1 right-hand-side outcome variable-switching between per-capita and inverse-sine is a bit confusing and inconsistent. I understand it's up to the researcher to choose which one to use, but I am unsure which to choose. I find similar results with both.

* I am curious about your opinions on what is happening in my regression specification when I add/subtract a couple of the covariates (SAT score + proportion foreign). I lose observations when I include both, which I think may be driving the results to be significant. However, I can also argue for keeping these controls in as they will compare universities that are more similar to one another. For instance, a university that has more international students is likely to have a different atmosphere than one with no international students. 

* Should I even have controls outside of fixed effects? One paper that I follow closely [@lindo_college_2018], does not include control variables for the schools characteristics. 


* In my event study, I omit one of the universities that has 2 moratoriums: University of Central Florida. I do this because I only have 2 months of pre-trends for the first closure. However, I know that if I exclude this in my event study, I should exclude it in my results as well. Yet I don't know if it's worth deleting a school that has 2 moratoriums. I am already underpowered, and don't want to give up more observations than I absolutely have to.

\section{Planned Next Steps/Directions}

* I have begun FOIA hazing violations to use as another outcome variable.

* I still have the NIBRS which has daily level data on crime reports which include age of victim, and time of incident. NIBRS will shrink my sample size to include only 18 universities, but it will still be a nice check.

* I want to wait until I have my final covariates before starting to build a story of how effective moratoriums are at reducing reports of rape. I could run the analysis using my incomplete data, but I do not want results to sway which way I paths I begin to analyze.

* Once I have more of my results, I'll do a more in-depth literature review to build around my story.


\newpage
\section*{References} 
\parindent0pt <div id="refs"></div>


\newpage

```{r tables, include = F}
## Table-orischools table
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Tables/orischools_table.R")
## Table - summary statistics
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Tables/summary_stats.R")
## Triggering event table
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Tables/trigger_table.R")
## CLosure table
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Tables/table_1_closure_times.R")
```

```{r figures, include = F}
## map
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/map.R")
## event study
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/event_study_1.R")
## boxplot
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/boxplot_police_departments.R")
```

```{r cleared, include = F}
## rapes cleared
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/rapes_cleared_regressions.R")
```

```{r regression, include = F}
## both university and municipalities
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/primary_regressions_percap.R")
```

```{r regression2, include= F}
source("/Users/michaeltopper/Desktop/Fraternities and Sexual Assault/Figures/primary_regressions_inverse.R")
```


```{r closuretable, echo = F}
kable(closure_table, caption = "Fraternity Moratorium Closure and Reinstated Dates", booktabs = T) %>%
  kable_styling(latex_options = "scale_down") %>% 
  kableExtra::landscape()

```

```{r orischools, echo = F}
kable(orischools_table, caption = "Universities and their corresponding police municipalities", booktabs = T) %>% 
  kable_styling(latex_options = "scale_down") 
```

```{r summarystats, echo = F}
kable(summary_stats, caption = "Averages of the 34 universities' attributes over the years 2013-2018", booktabs = T)
```

```{r clearancetest, echo = F}
indirect_test
```

```{r model1, echo = F}
model_2 %>% 
  kable_styling(latex_options = "scale_down") %>% 
  kableExtra::landscape()
```

```{r, echo = F}
models %>% 
  kable_styling(latex_options = "scale_down") %>% 
  kableExtra::landscape()
```







\newpage

\begin{figure}
	\centering
	 \includegraphics[width = \linewidth]{SigmaAlpha.png}
	 \caption{The fraternity chapter, Sigma Alpha Episilon, guidelines for members.}
	 \label{fig:sigmaalpha}
\end{figure}

```{r, fig.cap = "\\label{map}Distribution of fraternity moratoriums in the sample from years 2013-2018. Each dot represents the average of yearly per-capita reports of rape by the jurisdictions serving the universities.", fig.pos="H", echo = F}
per_capita_map
```


```{r, fig.cap = "\\label{triggerevent}Distribution of triggering events for university moratoriums. The *Other* category represents triggering events such as alcohol violations, re-evaluation due to national trends, and unspecified rule violations.", fig.pos="H", echo = F}
trigger_figure
```

```{r, fig.cap = "\\label{boxplot}Distribution of per-capita reports of rape by type of police municipality."}
boxplot_department
```

```{r, fig.cap = "\\label{eventstudy}Event study showing 8 months prior and 2 months post moratorium.", out.width='.49\\linewidth', fig.ncol = 2, fig.subcap =  c("Inverse-sine", "Per-capita rape"), fig.pos="H", echo = F }

coefs_inverse_plot
coefs_percap_plot
```
