---
title: "Appendix  C"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```
# Is the Share of Students in a Fraternity Important for Effectiveness? \label{asection:fraction}

In this appendix, I analyze whether universities with a higher fraction of undergraduates belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of their student population with IFC membership. Recall from Table \ref{summary_stats} that the fraction of undergraduate students with IFC membership can range from 1% to as high as 11%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

To conduct this analysis, I supplement the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the earliest recorded count of IFC fraternity members over 2014-2019 at university $u$, divided by the undergraduate enrollment, and centered at its mean. I use the earliest count of IFC members for two reasons; first, to avoid the potential issue of declines in IFC membership after a moratorium due to permanent suspensions of specific IFC chapters, and second, many universities do not maintain records of IFC numbers for every year in the sample period. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations.^[West Virginia University is an exception to this. Their official IFC count decreased by over 60 percent in years following the moratorium.] Therefore, an early one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a more intense treatment than universities with lower shares.

Table \ref{ifc_share} reports evidence that moratoriums with a higher fraction of student enrollment belonging to an IFC fraternity exhibit larger decreases in alcohol offenses during a moratorium. In Column 1 of Panel A, the point estimate shows that a moratorium with a 10% higher share of IFC members results in a 0.023 decrease in the number of alcohol offenses per-25000 enrolled students. This effect is not statistically significant, although the effect is strongest on the weekends. Similarily, in Column 1 of Panel B, the point estimates for the interaction term show that moratoriums in universities with a higher share of IFC members exhibit larger decreases of sexual assaults. However, these decreases do not persist on weekends (Column 2) and none of the point estimates are statistically significant. Given the insignificance of the results, there is only evidence that the share of IFC members affects the impact of moratoriums.

```{r, echo = F, message = F, warning = F}
source(here::here("referee_analysis/ifc_frac_analysis.R"))
```
\newpage
```{r, echo = F, message = F, warning = F,fig.pos='H' }
ifc_share
```




