---
output: 
  pdf_document:
    number_sections: true
    extra_dependencies: ["flafter"]
indent: true
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage{bbm} ##for indicator
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage{framed}
- \usepackage{afterpage}
- \usepackage{geometry}
- \usepackage{indentfirst}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage{rotating}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\onehalfspacing
- \usepackage{subfig}
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \fancyhead[R]{JHR Submission 0722-12422}
- \floatplacement{figure}{H}
- \setcounter{section}{-1}
linkcolor: blue
bibliography: "references.bib"
link-citations: yes
nocite: |
  @kaplandata, @ucrbook, @cameron_bootstrap-based_2008
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(kableExtra)
library(bookdown)
library(modelsummary)
library(fixest)
library(grid)
library(gridExtra)
library(patchwork)
options(modelsummary_model_labels="model")
```

\noindent I respond to all editor and referee comments in this document. I have created sections and subsections in order to help organize the response. I also provide all figures and tables at the end of this document so that they can be linked to my responses to the comments and suggestions. Section \ref{section:editor} responds to the suggestion from the editor. Section \ref{section:ref1} includes responses to all comments and suggestions provided by Referee #1, Section \ref{section:ref2} responds to comments and suggestions from Referee #2, Section \ref{section:ref3} responses to the report provided by Referee #3, and Section \ref{section:ref4} responds to suggestions from Referee #4. Note that all comments and suggestions from the referees are in boxes. Also, note that in the Appendices attached there are unlinked references. These references are correctly linked in the main paper, but could not be linked in this cover letter.

# Response to the Editor \label{section:editor}

## Suggestion for Improvement

\begin{framed}
\noindent Your analysis is a straight-up policy evaluation, which is fine and the JHR has published a number of papers of this type. Still, in their letters to me, all the reviewers raise the question whether this is an important enough question to warrant publication in the JHR. They fall on both sides of the divide, about equally split. R2 has perhaps the strongest concerns along those lines, which are outlined also in their comments to you. I believe it is an important question and goes to the core issue of whether university policies have any bite. However, the fact that all reviewers have the same concern signals to me that the importance of the question and the implications from your analysis could be emphasized more strongly and perhaps positioned in a somewhat wider literature.
\end{framed}

Thank you for your helpful insight on how to better phrase the core question of this paper. To emphasize the question and position this paper in a wider literature, I have revised the eighth paragraph (page 3) of the introduction as shown in the following excerpt. Note that the new material is in italics:


> More broadly, this paper adds to the literature in several bodies of work, the first of which is the effect of college partying. While the literature shows that college partying increases daily reports of rape and alcohol offenses when using football game variation [@lindo_college_2018], this study more directly focuses on a policy tool that reduces college partying. I later analyze in Section 7.1 whether moratoriums have mitigating effects on college partying behavior when coinciding with college football game-days, although I find no clear evidence in support of this. *Second, this paper contributes to an emerging body of economic work relating to the effectiveness of both university policy, and more specifically, fraternity policy. Although broad university policies such as academic probation [@lindo_alcohol_2013] and financial aid [@dynarski_does_2003] have been found to be effective in improving GPA and recruiting students respectively, there are only two studies as of this writing that analyze fraternity-targeted policies which both study the effects deferring fraternity recruitment from freshman to sophomore year [@de_donato_effects_2017;@even_greek_2020]. Notably, neither of these policies focus on university crime.* Currently, only one related work has focused on fraternities and crime [@raghav_greek_2021], although this study focuses on how the size of a fraternity population effects campus crime rather than the effect of a typical fraternity policy. Last, this paper adds to the literature relating to the effects of alcohol on college-aged individuals which include health effects, such as increases in mortality [@carpenter_effect_2009] , emergency room visits [@francesconi_liquid_2019], *and adolescent brain development [@silveri_adolescent_2012]*, and behavioral effects, such as increases in crime [@carpenter_minimum_2015] and hindering academic performance [@carrell_does_2011;@ha_legal_2019].

In addition to this change, I have updated the nomenclature of the original model in Equation \ref{main_model} shown on page 11. The treatment variable now reads $InMoratorium_{u,t}$ rather than $Moratorium_{u,t}$ to more consistently align with the tables and figures. The equation now reads:

\begin{equation}\label{main_model}
Y_{u,t} = \beta InMoratorium_{u,t}  + \gamma_{u} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}
\end{equation}


# Response to comments from Referee #1 \label{section:ref1}

## Suggestion for Improvement
\begin{framed}

\noindent In the section about spillover analysis using Campus Safety and Security (CSS) data, the author has not specified if they used arrests for liquor law violations, disciplinary actions for liquor law violations, or some (weighted) average of both. Under Clery Act 1990, both the number of arrests and the number of disciplinary actions in residence halls (and elsewhere) are collected and reported by colleges and universities. However, the author has failed to specify which of the two they have used in this section of the paper. Not only should the author clearly specify which of these two variables is being used for the analysis in this section, but I would suggest that the author run separate analyses using each of the two variables (the number of arrests and disciplinary actions due to liquor law violations in residence halls) so that the reader can get some additional insights.
\end{framed}

This is an excellent suggestion as the delineation between disciplinary actions and arrests is important for interpretation, clarity, and replication purposes. In the reviewed draft, the Campus Safety and Security (CSS) analysis uses disciplinary actions for liquor law violations and excludes arrests. As suggested, I have extended the analysis to include both disciplinary actions and arrests for liquor law violations in Appendix \ref{asection:spillovers} and updated the final two paragraphs of Section 5.2 with additional commentary. Both of these extensions are further explained in the following paragraphs.

In Appendix Table \ref{css_arrests}, I delineate between disciplinary actions and arrests in the CSS data for alcohol offenses by adding Columns 4 and 5 which analyzes the effect of moratoriums on arrests for all reports in the CSS and residence hall incidents respectively. Columns 4 and 5 show that there is little evidence of arrests changing at universities, regardless of the location. In particular, for each additional moratorium day in a calendar year, alcohol arrests per-25000 enrolled students do not exhibit any statistically significant decrease and the point estimates are relatively small when compared to disciplinary actions. This is consistent with the literature that campus police do not commonly arrest students for underage drinking [@bernat_college_2014]. Hence, while there is evidence that moratoriums affect student alcohol behavior, there is little evidence that moratoriums affect arrests for alcohol violations. In light of these findings, I update the final paragraph of Appendix \ref{asection:spillovers} to reflect this analysis:

> However, there is little evidence of an effect on liquor law arrests as shown in Columns 4 and 5—consistent with the literature that campus police do not typically arrest students for alcohol violations [@bernat_college_2014]. As discussed in Section 5.2, this supports the notion that if moratoriums displace alcohol-fueled behavior, they displace it to *less* risky areas whereby behavior can more easily be intervened before it becomes dangerous.

Given the lack of significance and small point estimates in the arrest columns, I update the final two paragraphs of Section 5.2 to address the delineation between arrests and disciplinary actions and save the additional analysis of arrests for Appendix \ref{asection:spillovers}. However, I am happy to move the analysis to the main paper upon the editor's request. The following is an excerpt from the updated Section 5.2 in the main paper:

> As the second set of analysis, I analyze the CSS data to examine if students substitute partying at fraternity houses to different on-campus locations during moratoriums. The CSS data contains all disciplinary actions and arrests corresponding to liquor law violations in addition to reports of sexual assaults that occur in a calendar-year...

\noindent The extension continues in the final paragraph where I more directly assert the findings:

> Using the CSS data, there is evidence that moratoriums move drinking from fraternity houses to residence halls. Residence halls show a 0.270 *increase* in yearly disciplinary actions of alcohol offenses for each additional moratorium day in a calendar-year. Interestingly, this is accompanied by a 0.033 *decrease* in yearly residence hall sexual assault reports.

Finally, the text of Appendix \ref{asection:spillovers} more closely describes the CSS data used and the corresponding results. As noted at the beginning of the document, the appendices are included at the end of this document for convenience.

\newpage

# Response to comments from Referee #2 \label{section:ref2}

## Suggestion #1: Weighting 

\begin{framed}
I'm not sure the results are strong enough. Qualitatively, the results are unsurprising - banning activities with involve alcohol will likely reduce crimes which involve alcohol. Quantitatively, the results are imprecise, and hence difficult to interpret confidently. The point estimates seem very large, alcohol related crimes reduced by 26\% despite the fraction of the students enrolled in IFC fraternities being less than 5\%. I'm not dismissing this magnitude as unfeasible - especially if the author could show some more supplementary evidence on the likely share of such crimes that are associated with fraternities. However, the CIs are wide, and do not rule out very small effects, so it is not clear whether or not the effects are actually 'large'. Of course these issues are true to a greater extent for the more imprecise results for sexual assault. 

Two suggestions which may improve precision: To weight by total enrollment (or perhaps undergraduate enrollment if you feel that is more appropriate). Larger schools should have less residual variation, so weighting by size should reduce standard errors. The variance in school size should be large enough for this to make a difference.
\end{framed}


Thank you for the thoughtful suggestion on how to tighten/strengthen the main results of the paper. First, I agree that despite the large point estimates, the standard errors do not rule out small effects. To reconcile this, I have deleted all language where I describe the effects as large. However, as pointed out, these estimates are not unfeasible. Although the data cannot delineate whether an incident is associated with fraternities, non-members are also likely affected by moratoriums as fraternity parties are a substantial source of partying for all undergraduates [@harford_attendance_2002]. Moreover, the magnitude (29% on weekends) for the decreases in sexual assaults are in-line with the increases (28%) found due to intensifying partying in @lindo_college_2018. 

Second, as recommended, I have explored weighting by total enrollment to tighten the main results. Unfortunately, the weights do not tighten the results to a significant degree. However, the results remain extremely consistent with their unweighted counterpart. I elaborate more in the following paragraphs.

Table \ref{main_table_weighted} shows the estimations of Table \ref{main_table} (the main results table) with total enrollment weights. The preferred specification reported in Column 2 of Panel A shows that the point estimates are nearly identical to the unweighted estimation for alcohol offenses, exhibiting a 26.5% decrease from the mean rather than a 27.8% decrease. Furthermore, the standard errors are reduced minimally, ruling out decreases smaller than 5.6% (weighted) rather than 4.3% (unweighted) with 95% confidence. Similarly, in Column 2 of Panel B, sexual assaults exhibit a 16% decrease—a four percentage point drop from the 20% decrease shown in the unweighted estimation. While this result is now significant at the 10% level, the change in p-value from unweighted to weighted is small with a difference of 0.04. Moreover, the weekend analysis in Column 4 also remains consistent across both weighted and unweighted regressions for each offense. In particular, alcohol offenses show a 29.3% decrease from the mean (weighted) rather than a 28.7% decrease (unweighted) and the standard errors rule out decreases smaller than 4.1% (weighted) rather than 2.6% (unweighted). For sexual assaults, weekends with moratoriums show a 32.7% decrease from the mean (weighted) rather than a 29.3% decrease (unweighted). Note that the p-value decreases as well, with the unweighted weekend estimation showing a p-value of 0.021 (5% significance) instead of 0.091 (10% significance). 

To maintain transparency, I have included the weighted regressions in Appendix \ref{section:appendixf}. In addition, I have also alluded to these estimations when discussing the main results in paragraph three of Section 5.1 which reads: 

> Third, due to the large variation in university size, I weight the models in Table \ref{main_table} by total enrollment in Appendix Table \ref{main_table_weighted}. The weighted estimations exhibit similar results to the unweighted models—alcohol offenses and sexual assaults decrease by 29 and 32 percent on the weekends respectively, while the standard errors remain similar in magnitude.

Last, for ease of comparison between the weight and unweighted results, I have included a figure that is unique to this cover letter in Appendix Figure \ref{main_table_graphic_weighted}. In this figure, I plot the point estimates and 95% confidence intervals for each of the columns in Table \ref{main_table} (unweighted) and Table \ref{main_table_weighted} (weighted). The figure demonstrates that the results are largely similar with minimal gains in precision across most specifications. Notably, Columns 3 and 5 of alcohol offenses lose precision when using the weighted estimations. 


## Suggestion #2: Leverage IFC Variation

\begin{framed}
To interact the treatment variable with the share of students who are in IFC fraternities. Perhaps I'm missing something, but I would expect the effect size to be essentially proportional to the proportion in IFC fraternities. To be clear, I'm suggesting replacing Moratorium (in equation 1) with Moratorium * Fraction\_IFC.
\end{framed}

This is a great suggestion, also proposed by Referee #4. Prompted by this suggestion, I have  collected the additional data needed for this analysis as I was previously missing four universities' IFC population numbers. I append Section 6.1, "Do Party Schools Exhibit the Strongest Effects?" with a small discussion on this analysis:

> Similarly, Appendix \ref{asection:fraction} explores whether universities that have relatively more *fraternity* life—defined by the fraction of undergraduate students enrolled in an IFC—display larger effects. By supplementing the preferred specification with an interaction between the $InMoratorium_{u,t}$ treatment variable and the fraction of undergraduates in an IFC fraternity, there is evidence that universities with more fraternity life show larger declines in alcohol offenses during moratoriums. Although statistically insignificant, the point estimates are negative, thereby hinting at the possibility that moratoriums are more effective when a higher fraction of students are directly affected by its guidelines.

As alluded to in the excerpt, I include a more thorough discussion of this exercise in the newly added Appendix \ref{asection:fraction}. This thorough discussion is omitted from the main paper due to the statistically insignificant results. I have copied text from the new Appendix \ref{asection:fraction} in what follows:


> In this appendix, I analyze whether universities with a higher fraction of undergraduates belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of their student population with IFC membership. Recall from Table \ref{summary_stats} that the fraction of undergraduate students with IFC membership can range from 1% to as high as 11%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

> To conduct this analysis, I supplement the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the earliest recorded count of IFC fraternity members over 2014-2019 at university $u$, divided by the undergraduate enrollment, and centered at its mean. I use the earliest count of IFC members for two reasons; first, to avoid the potential issue of declines in IFC membership after a moratorium due to permanent suspensions of specific IFC chapters, and second, many universities do not maintain records of IFC numbers for every year in the sample period. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations.^[West Virginia University is an exception to this. Their official IFC count decreased by over 60 percent in years following the moratorium.] Therefore, an early one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a more intense treatment than universities with lower shares.

> Table \ref{ifc_share} reports evidence that moratoriums with a higher fraction of student enrollment belonging to an IFC fraternity exhibit larger decreases in alcohol offenses during a moratorium. In Column 1 of Panel A, the point estimate shows that a moratorium with a 10% higher share of IFC members results in a 0.023 decrease in the number of alcohol offenses per-25000 enrolled students. This effect is not statistically significant, although the effect is strongest on the weekends. Similarily, in Column 1 of Panel B, the point estimates for the interaction term show that moratoriums in universities with a higher share of IFC members exhibit larger decreases of sexual assaults. However, these decreases do not persist on weekends (Column 2) and none of the point estimates are statistically significant. Given the insignificance of the results, there is only evidence that the share of IFC members affects the impact of moratoriums.


\newpage

# Response to comments from Referee #3 \label{section:ref3}

## Major Comment 1: Effect of a Death

\begin{framed}
In reading the manuscript, I was initially concerned that the author was not going to address the critical assumption that a triggering event that may lead to a moratorium does not also lead students to change their behavior in ways that would reduce alcohol offenses or sexual assaults - the outcomes of interest. It is plausible that the death of a peer as a result of risky behavior at a fraternity would lead students at the university to at least temporarily change their behavior in ways that would reduce alcohol offenses and sexual assaults. This concern would seem to merit discussion in section 4.2 "Identification Assumptions". While the author addresses the concern that the timing of fraternity moratoriums are as-good-as-random, it would seem equally important that the triggering event is not influencing both existence of a moratorium and the outcomes of interest. This analysis, that was critical for me to view the estimated effects as credibly causal, comes at the very end of the paper in section 6.2. This section "Does the Triggering Event for a Moratorium Matter?" primarily focuses on whether it matters if the triggering event is "...the result of a fraternity-related death, a prominent sexual assault, or a behavior violation." Finally, the author gets to the critical statement on page 24 "To ensure that this is the effect of the moratorium rather than the triggering death, Appendix Figure C7 shows the preferred specification restricted to only the universities that experienced a fraternity-related death with an additional 15 universities that experience a fraternity-related death in the same period, but did not undergo a moratorium." These additional universities and their experiences with a fraternity-related death but no moratorium provide a valuable comparison group. I believe the author needs to clarify the estimation equation used in this figure - I am assuming the author did what I would hope, but found the text and note in the figure less than clear. I also believe the author needs to put a greater spotlight on this issue and more clearly present the results, even if it weakens the findings. The results would still be important. However, as a college administrator considering a moratorium, I want to clearly understand the best estimate for how much I would be expected to reduce alcohol violations and sexual assaults by implementing a moratorium after a fraternity-related death of a student - beyond any expected reduction resulting from just the triggering event. The estimated impact of moratoriums on sexual assaults, in Figure C8, are not even explicitly mentioned in the text for this specification and sample.
\end{framed}

Thank you for the excellent comment on this work. I agree that it is indeed plausible that the effect of a death—rather than the moratorium itself—could be contributing to the reductions in alcohol offenses that this paper shows and needs greater emphasis for the main results to be interpreted as causal. As suggested, I have highlighted this concern in Section 4.2 by including it as an additional assumption of the model (see page 12). I have also included a more in-depth discussion of this assumption in paragraph 6 of Section 4.2 which more directly responds to this concern:

> To evaluate the third assumption that the triggering event is not changing student behavior, I perform heterogeneity analysis in Section 6.2 and analyze the effect of a moratorium by each triggering event. As discussed further in Section 6.2, I find that the main results are driven by moratoriums that are triggered by fraternity deaths. While it is plausible that the shock of a death, rather than a moratorium, contributes to behavior changes in students, I construct a sample of 15 universities that undergo a fraternity-related death *without* a moratorium and assign a 64-day treatment (the average length of a moratorium) starting with the day of the death. In doing so, I find little evidence that alcohol offenses or sexual assaults decrease due to the shock of a death.

As alluded to in the excerpt above, I conduct a stronger test of the triggering event assumption in Section 6.2 using a suggestion from Referee #4 in which I estimate the main specification with the 15 universities that undergo a fraternity-related death but do not undergo a moratorium. This test is distinct from the previous weak test that used these 15 universities as never-treated control units and more directly tests the effect of a death without a moratorium. Therefore, I have removed the old test, as this new analysis provides clearer evidence that the event of a death does not contribute to decreases found in the main results. Additionally, as suggested, Appendix Figures \ref{alc_forest} and \ref{sex_forest} have been reworked organizationally to more clearly delineate between the different samples: Panel A includes the main sample, Panel B includes the main sample with the addition of never-treated units, Panel C includes only the 15 universities that experience a fraternity-related death, but do not undergo a moratorium, and Panel D includes the universities from Panel C, with the addition of the never-treated units that were included in Panel B to increase power. 

Last, as suggested, I have updated Section 6.2, paragraph 2, to discusses this analysis in greater detail:

> Figure \ref{trigger_reg_graph} reports that the effect of moratoriums is more prominent when the corresponding trigger is a death or sexual assault rather than a behavior violation. In particular, alcohol offenses decline significantly when a fraternity-related death is the triggering event. To ensure that this is the result of the moratorium rather than the triggering death, I use an additional 15 universities that experienced a fraternity-related death in the sample period, but *did not* undergo a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities are those whose students experience the effect of a fraternity-related death, but do not experience a moratorium. First, I exclusively analyze these 15 non-moratorium universities by creating a 64-day binary treatment variable, beginning with the date of the death. A 64-day period is chosen as it is the average length of a moratorium. Next, I estimate the preferred specification using the 64-day period after the death in lieu of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by including the 14 never-treated schools that are used in Section 5.3 as never-treated controls for the effect of a death. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related death contributes to the decreases shown in alcohol and sexual assault offenses during a moratorium. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.


## Major Comment 2: Progression of a Moratorium

\begin{framed}
The author also suggests that the finding might inform administrators of the potential benefit of making a moratorium permanent. To address this question and to provide further evidence that the moratorium is causing the change and not the triggering event, I believe the author should also consider further examination of the variation in the length of the moratoriums. The author does explore the average daily effect of moratoriums across three lengths (Table 6). I was rather surprised to find the shortest moratoriums to have no effect (and a positive point estimate on alcohol offenses). Presumably none of these short moratoriums were due to a student death? As a reader, I was certainly left wondering if this was due to the type of triggering event. What I was hoping to see was an analysis that explicitly examined whether there are heterogenous impacts of the moratorium by how long it has been in effect. Over time, does the effect diminish within the moratorium? My understanding of the analysis is that the author explores different periods after the conclusion of a moratorium, but not different time periods within the moratorium. In Table 6, I don't know if the large negative impact on alcohol offenses are occurring evenly across the moratorium or primarily during the first 30 days. For policy implications, it would be incredibly valuable to understand when the reductions of alcohol offenses occur within the moratorium. This would inform both the optimal length of a moratorium and whether we would expect any benefit from a permanent ban on alcohol at these events.
\end{framed}

I agree that this suggestion gives valuable information for school administrators to more effectively plan their moratorium length. I have added an additional section which describes the analysis to address this suggestion in Section 5.4:

>Although moratoriums decrease alcohol offenses when implemented, it is within reason that these decreases are not uniform across the enforcement period. For instance, during a long moratorium, students may create alternatives to fraternity parties or overseers may become more lenient as time progresses. Therefore, it is important to understand both when and how long a moratorium is most effective, as this can better inform future moratorium length among school administrators. 

>To understand the progression of a moratorium's effectiveness, I split the $InMoratorium_{u,t}$ treatment variable into weekly bins for the first 9 weeks of a moratorium and pool the remaining weeks into one bin (Moratorium Weeks 10+) as shown in Panel A of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}.^[Note that 9 weeks is approximately the average length of a moratorium.] This amounts to 10 unique coefficients, each identifying the effect of the moratorium in the corresponding week. However, since moratorium lengths differ by university, each point estimate is identified by a dynamic number of schools as shown in parenthesis on the x-axis. For example, the coefficient identifying the effect of a moratorium in Week 3 is identified by 33 universities that have a moratorium that reach the 3-week length. Note that if a university has, for instance, a 22-day moratorium, this moratorium will contribute only one day to the identification of the Moratorium Week 4 coefficient.

>Panel A of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}, exhibit evidence that moratoriums are most effective in the first five weeks. In Panel A of Figure \ref{alc_passing_graph}, alcohol offenses show statistically significant declines at the 5% level in weeks one, two, and five of a moratorium. The effectiveness appears to trend upward after the fifth week, thereby suggesting that moratorium effectiveness may diminish over time. Similarly, sexual assaults show statistically significant declines in weeks one and three in Panel A of Figure \ref{sex_passing_graph}, while the effects appear to fade in later weeks.

>Although Panel A shows the by-week effect, it is possible that the significant declines in the first five weeks are driven by universities that have short moratoriums. To ensure that the trends are consistent across universities, I re-estimate the coefficients with only universities that have moratoriums over 9 weeks long in Panel B of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}. In each figure, Panel B shows similar trends to Panel A, although less precise due to the loss of power. This suggests that long moratoriums exhibit the strongest effects in the early weeks of implementation, and similarly, the effects diminish after the five weeks. 


## Major Comment 3: Update Table 7

\begin{framed}
To better interpret the results in Table 7, it would be helpful to know about the relative mean number of alcohol offenses at party schools versus non-party schools outside of a moratorium. It is possible for the reader to calculate this between the text in the second paragraph in section 6.1 and the information on Table 7, but it would be easier if it was provided. It would also highlight for the reader that party schools (as determined by the external rankings) do have more alcohol offenses per-25000 students than non-party schools.
\end{framed}

Thank you for this comment as it will certainly help readers better understand the amount of alcohol offenses/sexual assaults at party schools relative to non-party schools outside of a moratorium. I have added an additional paragraph in Section 6.1 and have updated Table \ref{party_school_table} with the non-moratorium means to help highlight the fact that party schools have more alcohol offenses per 25000 students than non-party schools. I have included the paragraph below for convenience:

> As shown in Table \ref{party_school_table}, universities defined as party schools exhibit higher averages of alcohol offenses assaults relative to non-party schools. In particular, non-party schools experience approximately 49% less alcohol offenses on average. These differences are similar when excluding moratorium days (47%), although both party schools and non-party schools have relatively similar levels of sexual assaults.

\newpage

# Response to comments from Referee #4 \label{section:ref4}

## Major Suggestion 1: Leverage IFC Variation
\begin{framed}
Currently, the main specification treats all moratoriums the same. However, presumably a moratorium at a school with 1.3\% of the body in IFC fraternities is less impacted by a moratorium than one with 10.2\% IFC membership. Can you provide heterogeneity analysis that probes this difference in intensity of treatment? This could be accomplished by interacting moratorium with share IFC or looking at quartiles of share IFC etc. 
\end{framed}

Thank you for this thoughtful suggestion. Given that Referee #2 had the same suggestion, I copy my response in the following paragraphs for your convenience:

I have collected the additional data needed for this analysis as I was previously missing four universities' IFC population numbers. I append Section 6.1, "Do Party Schools Exhibit the Strongest Effects?" with a small discussion on this analysis:

> Similarly, Appendix \ref{asection:fraction} explores whether universities that have relatively more *fraternity* life—defined by the fraction of undergraduate students enrolled in an IFC—display larger effects. By supplementing the preferred specification with an interaction between the $InMoratorium_{u,t}$ treatment variable and the fraction of undergraduates in an IFC fraternity, there is evidence that universities with more fraternity life show larger declines in alcohol offenses during moratoriums. Although statistically insignificant, the point estimates are negative, thereby hinting at the possibility that moratoriums are more effective when a higher fraction of students are directly affected by its guidelines.

As alluded to in the excerpt, I include a more thorough discussion of this exercise in the new Appendix \ref{asection:fraction}. This thorough discussion is omitted from the main paper due to the statistically insignificant results. I have copied text from the new Appendix \ref{asection:fraction} in what follows:


> In this appendix, I analyze whether universities with a higher fraction of undergraduates belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of their student population with IFC membership. Recall from Table \ref{summary_stats} that the fraction of undergraduate students with IFC membership can range from 1% to as high as 11%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

> To conduct this analysis, I supplement the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the earliest recorded count of IFC fraternity members over 2014-2019 at university $u$, divided by the undergraduate enrollment, and centered at its mean. I use the earliest count of IFC members for two reasons; first, to avoid the potential issue of declines in IFC membership after a moratorium due to permanent suspensions of specific IFC chapters, and second, many universities do not maintain records of IFC numbers for every year in the sample period. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations.^[West Virginia University is an exception to this. Their official IFC count decreased by over 60 percent in years following the moratorium.] Therefore, an early one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a more intense treatment than universities with lower shares.

> Table \ref{ifc_share} reports evidence that moratoriums with a higher fraction of student enrollment belonging to an IFC fraternity exhibit larger decreases in alcohol offenses during a moratorium. In Column 1 of Panel A, the point estimate shows that a moratorium with a 10% higher share of IFC members results in a 0.023 decrease in the number of alcohol offenses per-25000 enrolled students. This effect is not statistically significant, although the effect is strongest on the weekends. Similarily, in Column 1 of Panel B, the point estimates for the interaction term show that moratoriums in universities with a higher share of IFC members exhibit larger decreases of sexual assaults. However, these decreases do not persist on weekends (Column 2) and none of the point estimates are statistically significant. Given the insignificance of the results, there is only evidence that the share of IFC members affects the impact of moratoriums.




## Major Suggestion 2: Separating Effect of Triggering Event \label{section:death_sug}

\begin{framed}
One interesting result is that impacts of moratoriums seem larger 
following a student death (Figure 8). This begs the question of whether the incident (death) changes behavior for a short time, or whether the moratorium changes behavior. I would like to see whether a death without a moratorium causes a change in alcohol and sexual assault violations. Can you test this hypothesis by considering the 64 days (avg moratorium length) after these deaths as treated? 
Note – this suggestion is distinct from the test conducted in Appendix C7. I want to know 
whether a death causes a treatment effect absent a moratorium. Your test in C7 shows a related but separate idea—that moratoriums still cause a treatment effect when compared to colleges that have deaths but no moratoriums. Given that a large portion of the observations for a school with only a death would still be considered “untreated” (days prior to the event or days after the treatment period ended) even if it had a moratorium, the test in C7 may be a weak test, and I would encourage you to use more conservative language in describing the results. 
\end{framed}

This is a very thoughtful suggestion that certainly strengthens the paper. As requested, I estimate the main specification with the 15 universities that undergo a fraternity-related death but do not undergo a moratorium. I create a binary 64-day treatment variable that starts with the day of the death for each university. The results of this test are shown in Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest}. Ultimately, there does not appear to be evidence of a death-effect, and I further describe this analysis in the proceeding paragraphs. 

Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is no statistically significant effect when considering a 64-day period after a fraternity-related death. In Panel C of Appendix Figure \ref{alc_forest}, alcohol offenses show small, and positive point estimates, while in Panel C of Appendix Figure \ref{sex_forest}, sexual assaults show negative point estimates when considering all days of the week and on the weekdays. This provides evidence that the moratorium is producing the effects shown in the main results, rather than the triggering event itself. While moratoriums that are the result of a fraternity related death drive the results as discussed in Section 6.2, this may be due to students more-seriously abiding by the moratorium guidelines. 

Given the results and intuitive nature of this test, I believe that this analysis is better suited for the paper than the previous material I presented which utilized these 15 universities as never-treated control units. Therefore, I have omitted the old analysis in lieu of the new analysis shown in Appendix Figures \ref{alc_forest} and \ref{sex_forest}. Moreover, Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} also show an extension of this analysis by including the never-treated groups discussed in Section 5.1. This inclusion of never-treated units is motivated by the relatively small number of clusters (15) in the initial analysis and is performed to increase precision. Although precision is minimally increased, the results remain consistent nonetheless.

Please note that Section 6.2 has now been updated to reflect the suggestions and subsequent analysis. What follows is the updated passage from Section 6.2, paragraph 2, which discusses this test and the results:

> Figure \ref{trigger_reg_graph} reports that the effect of moratoriums is more prominent when the corresponding trigger is a death or sexual assault rather than a behavior violation. In particular, alcohol offenses decline significantly when a fraternity-related death is the triggering event. To ensure that this is the result of the moratorium rather than the triggering death, I use an additional 15 universities that experienced a fraternity-related death in the sample period, but *did not* undergo a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities are those whose students experience the effect of a fraternity-related death, but do not experience a moratorium. First, I exclusively analyze these 15 non-moratorium universities by creating a 64-day binary treatment variable, beginning with the date of the death. A 64-day period is chosen as it is the average length of a moratorium. Next, I estimate the preferred specification using the 64-day period after the death in lieu of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by adding the 14 never-treated schools that are used in Section 5.3 as never-treated controls for the effect of a death. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related causes a decrease in alcohol or sexual assault offenses rather than the moratorium itself. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.


## Major Suggestion 3: Representativeness

\begin{framed}
It would be helpful to place the sample in context relative to the Greek-life ecosystem to comment about generalizability. For instance, what is a typical share IFC across all 4-year US colleges and universities and how does this differ from the sample? Some small private colleges have very large Greek presence in percentage terms (e.g. Depauw University is \~70\% Greek), but these schools are largely unrepresented in the sample. Would we expect results to generalize etc.? 
\end{framed}

Unfortunately, there does not exist a data repository of IFC fraternity populations at the university level—the North American Interfraternity Conference (NIC) has informed me that they do not track such records. Moreover, the [US News Rankings of universities with the highest share of men in fraternities](https://www.usnews.com/best-colleges/rankings/most-frats), has two major shortcomings: first, it only reports percentages for 100 universities in the US, many of which are small universities. Second, and most importantly, the US News Rankings does not specify whether their statistics are based on strictly IFC fraternities. Recall from Section 2.1 that there are other types of fraternities such as academic, professional, and service fraternities. Although the statistics that I have collected for universities that are in both the list and sample align (for instance, I find Rollins College has 23% of their undergraduate male population as a member of an IFC fraternity, and the list finds 22%), I would prefer to remain cautious about this source of data given its lack of clarity.^[Please note that in the paper I report the fraction of undergraduate enrollment belonging to an IFC community rather than the fraction of undergraduate males which is why the maximum number I report in the summary statistics table is 11%.] 

However, I certainly agree that there is not enough context surrounding the sample universities and how they relate to other universities in terms of Fraternity/Sorority Life. To give context surrounding the importance of fraternities at the sample universities relative to other schools, I use the Best Greek Life Colleges in America ranking from Niche.com. These rankings are based on survey responses from Niche.com users on the quality of Fraternity/Sorority Life at their school and 300 universities nation-wide are ranked. Furthermore, this list is used in Section 5.1 of the paper as criteria for adding never-treated universities.

Figure \ref{niche_ranking_graph} shows that the 37 universities in the sample are generally representative of schools with high-fraternity activity with the schools exhibiting a median ranking (represented by the dashed red line) of 64. In addition, 14 of the 37 universities (38%) are ranked in the top 50, while only 5 of 37 (13%) are not ranked. This figure has been added to the appendix as well as an additional sentence referring to the figure in Section 3.3 which reads, "Although IFC members represent a small number of enrolled students, the universities in the sample are representative of schools with active Fraternity and Sorority Life (see Appendix Figure \ref{niche_ranking_graph})".

## Minor Suggestion 1: Condensing Sections 3.1 and 3.2
\begin{framed}
Sections 3.1 and 3.2 could be condensed with some of the material moved to the online appendix.
\end{framed}

Thank you for this suggestion to add conciseness to the paper. As recommended, I have shortened Sections 3.1 and 3.2 by approximately 500 words and moved extraneous details to a newly created Appendix \ref{asection:data}.


\newpage
# References

<div id="refs"></div>


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/figures.Rmd", fig.pos="H"}

```


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/tables.Rmd", fig.pos = "H"}

```



\newpage
# Appendix {-}

```{=tex}
\appendix
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{A\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_data.Rmd", fig.pos='H' }

```

\newpage

```{=tex}

\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{B\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_twfe.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{C\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_spillover.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{D\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_fraction_ifc.Rmd", fig.pos='H' }

```




\newpage
```{=tex}
\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{E\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```
```{r, child = "paper_iterations/working_paper_november_2022/appendix_figures.Rmd", fig.pos='H' }

```


\newpage

```{=tex}
\renewcommand{\thefigure}{F\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{F\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{F\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```
```{r, child = "paper_iterations/working_paper_november_2022/referee_figures.Rmd", fig.pos='H' }

```

