---
output: 
  pdf_document:
    number_sections: true
    extra_dependencies: ["flafter"]
indent: true
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage{bbm} ##for indicator
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage{framed}
- \usepackage{afterpage}
- \usepackage{geometry}
- \usepackage{indentfirst}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage{rotating}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\onehalfspacing
- \usepackage{subfig}
- \usepackage{placeins}
- \floatplacement{figure}{H}
linkcolor: blue
bibliography: "references.bib"
link-citations: yes
nocite: |
  @kaplandata, @ucrbook, @cameron_bootstrap-based_2008
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(kableExtra)
library(bookdown)
library(modelsummary)
library(fixest)
library(grid)
library(gridExtra)
library(patchwork)
```

\noindent I respond to all editor and referee comments in this document. I have created sections and subsections in order to help organize the response. I also provide all figures and tables at the end of this document so that they can be linked to my responses to the comments and suggestions. Section \ref{section:ref1} includes responses to all comments and suggested provided by Referee #1, Section \ref{section:ref2} responds to comments and suggestions from Referee #2, Section \ref{section:ref3} responses to the report provided by Referee #3, and Section \ref{section:ref4} responds to suggestions from Referee #4. 

### Small Update in the Paper

I have updated the nomenclature of the treatment variable in Equation 1 to read $InMoratorium_{u,t}$ rather than $Moratorium_{u,t}$ to more consistently match with the tables. The baseline specification model now reads:

\begin{equation}\label{main_model}
Y_{u,t} = \beta InMoratorium_{u,t}  + \gamma_{u} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}
\end{equation}

\noindent where $Y_{u,t}$ is an outcome of alcohol offenses or sexual assaults per-25000 enrolled students per academic-calendar day at university $u$ in time $t$. $InMoratorium_{u,t}$ is an indicator variable equal to one when university $u$ is undergoing a moratorium at time $t$, $\gamma_u$ is a university-specific fixed effect, $\mathbb{X}_t$ is a vector of time-varying controls that are shared across universities, and $\epsilon_{u,t}$ is the error term.

# Response to comments from Referee #1 \label{section:ref1}

## Suggestion for Improvement
\begin{framed}

\noindent In the section about spillover analysis using Campus Safety and Security (CSS) data, the author has not specified if they used arrests for liquor law violations, disciplinary actions for liquor law violations, or some (weighted) average of both. Under Clery Act 1990, both the number of arrests and the number of disciplinary actions in residence halls (and elsewhere) are collected and reported by colleges and universities. However, the author has failed to specify which of the two they have used in this section of the paper. Not only should the author clearly specify which of these two variables is being used for the analysis in this section, but I would suggest that the author run separate analyses using each of the two variables (the number of arrests and disciplinary actions due to liquor law violations in residence halls) so that the reader can get some additional insights.
\end{framed}

This is an excellent suggestion as the delineation between disciplinary actions and arrests is important for interpretation, clarity, and replication purposes. In the reviewed draft, the Campus Safety and Security (CSS) analysis uses disciplinary actions for liquor law violations and excludes arrests. As suggested, I have extended the analysis to include both disciplinary actions and arrests for liquor law violations in Appendix B and updated the final two paragraphs of Section 5.2 with additional commentary. Both of these extensions are further explained in the following paragraphs.

In Appendix Table \ref{css_arrests}, I delineate between disciplinary actions and arrests in the CSS data for alcohol offenses by adding Columns 4 and 5 which splits all reports and residence hall incidents respectively. Columns 4 and 5 show that there is little evidence of arrests changing at universities, regardless of the location. In particular, for each additional moratorium day in a calendar year, alcohol arrests per-25000 enrolled students do not exhibit any statistically significant decrease and the point estimates are relatively small when compared to disciplinary actions. This is consistent with the literature that campus police most commonly use arrests and other enforcement actions only when alcohol violations result in serious incidents such as an assault [@bernat_college_2014]. Hence, while there is evidence that moratoriums affect student alcohol behavior, there is little evidence that moratoriums affect serious alcohol behavior. In light of these findings, I update the final paragraph of Appendix B to reflect this analysis:

> However, there is little evidence of an effect on liquor law arrests as shown in Columns 4 and 5—consistent with the literature that campus police most commonly use arrests and other enforcement actions only when liquor law violations result in serious incidents such as an assault [@bernat_college_2014]. As discussed in Section \ref{section:spillover}, this supports the notion that if moratoriums displace alcohol-fueled behavior, they displace it to *less* risky areas whereby behavior can more easily be intervened before it becomes dangerous.

Given the lack of significance and small point estimates in the arrest columns, I update the final two paragraphs of Section 5.2 to address the delineation between arrests and disciplinary actions and save the additional analysis of arrests for Appendix B. However, I am happy to move the analysis to the main paper upon editor's request. The following is an excerpt from the updated Section 5.2 in the main paper:

> As the second set of analysis, I analyze the CSS data to examine if students substitute partying at fraternity houses to different on-campus locations during moratoriums. The CSS data contains all disciplinary actions and arrests corresponding to liquor law violations in addition to reports of sexual assaults that occur in a calendar-year...

\noindent The extension continues in the final paragraph where I more directly assert the findings:

> Using the CSS data, there is evidence that moratoriums move drinking from fraternity houses to residence halls. Residence halls show a 0.270 *increase* in yearly disciplinary actions of alcohol offenses for each additional moratorium day in a calendar-year. Interestingly, this is accompanied by a 0.033 *decrease* in yearly residence hall sexual assault reports.

\noindent Note that I also update the percentages in the sentence "on average, the Daily Crime Logs contain approximately 30% and 50% of the yearly alcohol offenses and sexual assaults reported in the CSS data respectively" to account for the addition of arrests in the CSS data analysis. 

Finally, the text of Appendix B more closely describes the CSS data used and the corresponding results. As noted above at the beginning of the document, the appendices are included at the end of this document for convenience.

\newpage

# Response to comments from Referee #2 \label{section:ref2}

## Suggestion #1: Weighting 

\begin{framed}
I'm not sure the results are strong enough. Qualitatively, the results are unsurprising - banning activities with involve alcohol will likely reduce crimes which involve alcohol. Quantitatively, the results are imprecise, and hence difficult to interpret confidently. The point estimates seem very large, alcohol related crimes reduced by 26% despite the fraction of the students enrolled in IFC fraternities being less than 5%. I'm not dismissing this magnitude as unfeasible - especially if the author could show some more supplementary evidence on the likely share of such crimes that are associated with fraternities. However, the CIs are wide, and do not rule out very small effects, so it is not clear whether or not the effects are actually 'large'. Of course these issues are true to a greater extent for the more imprecise results for sexual assault. 

Two suggestions which may improve precision: To weight by total enrollment (or perhaps undergraduate enrollment if you feel that is more appropriate). Larger schools should have less residual variation, so weighting by size should reduce standard errors. The variance in school size should be large enough for this to make a difference.
\end{framed}

Thank you for the thoughtful suggestion on how to tighten/strengthen the main results of the paper. In Column 3 of Table \ref{main_table}, I have included a column for the main specification weighted by total enrollment. As recommended, I have also explored weighting by undergraduate enrollment which gives similar results to total enrollment. However, I hesitate to include weights as the default for two main reasons. First, unfortunately, the weights do not tighten the results to a significant degree. Columns 2 and 3 of Table \ref{main_table} show the preferred specification, with the latter weighted by total enrollment. As displayed in Panel A, the standard errors and point estimates are nearly identical for alcohol offenses, exhibiting a 26.5% and 27.8% decrease from the mean respectively. Similarly in Panel B, sexual assaults exhibit a 20% decrease (statistically insignificant) and a 16% decrease (10% significance) in unweighted and weighted estimations. While the weighting enhances the sexual assault results to a small degree, I would prefer to be as conservative as possible, especially when discussing the effect alcohol offenses, which is the strongest and most robust result of the paper. Second, while I am pleased that the results are consistent, I am apprehensive that weighting all specifications will invite skepticism of the results. Hence, I believe that including the main specification, weighted and unweighted as shown in Columns 2 and 3, is a great solution to convince readers of the results and, in addition, follows the empirical suggestion of reporting both estimates as outlined in @solon_what_2015. However, upon request, I am more than happy to report the main results (weighted) from Table \ref{main_table} in an online appendix table. 

## Suggestion #2: Leverage IFC Variation

\begin{framed}
To interact the treatment variable with the share of students who are in IFC fraternities. Perhaps I'm missing something, but I would expect the effect size to be essentially proportional to the proportion in IFC fraternities. To be clear, I'm suggesting replacing Moratorium (in equation 1) with Moratorium * Fraction\_IFC.
\end{framed}

This is a great suggestion, also proposed by Referee #4. Initially, I withheld this analysis due to data restrictions—four universities previously were unresponsive to requests for their official IFC numbers and I did not want to confuse the reader with too many subsamples. Luckily, I have since collected the final information needed for this analysis and report the results in Section 6.3. Note that Section 6.3 is an entirely new section that was not previously included in the reviewed draft. I have copied text from the new Section 6.3 in what follows:

>   In this subsection, I analyze whether universities with a higher fraction of their student body belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of their student population attributed to IFC fraternities. Recall from Table \ref{summary_stats} that the fraction of enrolled students belonging to an IFC fraternity can range from 1% to as high as 10%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

>  To conduct this analysis, I replace the $InMoratorium_{u,t}$ treatment variable in the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the most recent number of IFC fraternity members at university $u$, divided by the average total enrollment over the sample period. I use the most current count of IFC members since most universities do not hold semester-level records of this information. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations. Therefore, a recent one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a larger treatment than universities with lower shares.

> Table \ref{ifc_share} reports that universities with a higher fraction of their student enrollment belonging to an IFC fraternity exhibit larger decreases in alcohol offenses during a moratorium. In Column 1 of Panel A, the point estimate shows that a 10% increase in the share of IFC members at a fraternity results in a 0.18 decrease in the number of alcohol offenses per-25000 enrolled students during a moratorium. This effect is statistically significant at the 5% level, and, similar to the main results, is strongest on the weekends. In Panel B, although not statistically significant, the point estimates for sexual assaults follow a similar pattern as alcohol offenses—universities with a higher fraction of IFC members in their study body exhibit larger decreases of sexual assaults. Taken together, a moratorium affects students' alcohol-behavior more when the restrictions apply to a greater share of the student body.

\newpage

# Response to comments from Referee #3 \label{section:ref3}

## Major Comment 1: Effect of a Death

\begin{framed}
In reading the manuscript, I was initially concerned that the author was not going to address the critical assumption that a triggering event that may lead to a moratorium does not also lead students to change their behavior in ways that would reduce alcohol offenses or sexual assaults - the outcomes of interest. It is plausible that the death of a peer as a result of risky behavior at a fraternity would lead students at the university to at least temporarily change their behavior in ways that would reduce alcohol offenses and sexual assaults. This concern would seem to merit discussion in section 4.2 "Identification Assumptions". While the author addresses the concern that the timing of fraternity moratoriums are as-good-as-random, it would seem equally important that the triggering event is not influencing both existence of a moratorium and the outcomes of interest. This analysis, that was critical for me to view the estimated effects as credibly causal, comes at the very end of the paper in section 6.2. This section "Does the Triggering Event for a Moratorium Matter?" primarily focuses on whether it matters if the triggering event is "...the result of a fraternity-related death, a prominent sexual assault, or a behavior violation." Finally, the author gets to the critical statement on page 24 "To ensure that this is the effect of the moratorium rather than the triggering death, Appendix Figure C7 shows the preferred specification restricted to only the universities that experienced a fraternity-related death with an additional 15 universities that experience a fraternity-related death in the same period, but did not undergo a moratorium." These additional universities and their experiences with a fraternity-related death but no moratorium provide a valuable comparison group. I believe the author needs to clarify the estimation equation used in this figure - I am assuming the author did what I would hope, but found the text and note in the figure less than clear. I also believe the author needs to put a greater spotlight on this issue and more clearly present the results, even if it weakens the findings. The results would still be important. However, as a college administrator considering a moratorium, I want to clearly understand the best estimate for how much I would be expected to reduce alcohol violations and sexual assaults by implementing a moratorium after a fraternity-related death of a student - beyond any expected reduction resulting from just the triggering event. The estimated impact of moratoriums on sexual assaults, in Figure C8, are not even explicitly mentioned in the text for this specification and sample.
\end{framed}

Thank you for the excellent comment on this work. I agree that it is indeed plausible that the effect of a death—rather than the moratorium itself—could be causing the reductions in alcohol offenses that this paper shows and needs greater emphasis for the main results to be interpreted as causal. As suggested, I have highlighted this concern in Section 4.2 by including it as an additional main assumption of the model. The assumptions now read "To estimate Equation \ref{main_model} and interpret $\beta$ as a casual effect of fraternity moratoriums, there are four main assumptions that need to be satisfied: the timing of fraternity moratoriums is as-good-as-random, there are no changes in reporting/policing during a moratorium, the triggering event is not changing student behavior, and moratoriums have no lasting effects." I have also included a more in-depth discussion of this assumption in paragraph 6 of Section 4.2. I have included the paragraph in what follows:

> To evaluate the third assumption that the triggering event is not changing student behavior, I perform heterogeneity analysis in Section \ref{section:trigger} and analyze the effect of a moratorium by each triggering event. As discussed further in Section \ref{section:trigger}, I find that the main results are driven by moratoriums that are triggered by fraternity deaths. While it is plausible that the shock of a death, rather than a moratorium, causes students to change their behavior, I construct a sample of 15 universities that undergo a fraternity-related death *without* a moratorium and assign a 64-day treatment (the average length of a moratorium) starting with the day of the death. In doing so, I find little evidence that alcohol offenses or sexual assaults decrease due to the shock of a death.

As alluded to in the excerpt above, I conduct a stronger test of the triggering event assumption in Section 6.2 using a suggestion from Referee #4 in which I estimate the main specification with the 15 universities that undergo a fraternity-related death but do not undergo a moratorium. I create a binary 64-day treatment variable that starts with the day of the death for each university. The results of this test are shown in Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest}. This test is distinct from the previous weak test of using these 15 universities as never-treated control units added to the main sample, and more directly tests the effect of a death without a moratorium. I have since removed the old test, as this new test provides clearer evidence of the lack of a death-effect. Second, Appendix Figures \ref{alc_forest} and \ref{sex_forest} have been reworked organizationally to more clearly delineate between the different samples: Panel A includes the main sample, Panel B includes the main sample with the addition of never-treated units, Panel C includes only the 15 universities that experience a fraternity-related death, but do not undergo a moratorium, and Panel D includes the universities from Panel C, with the addition of the never-treated units that were included in Panel B to increase power. 

Last, as suggested, I have updated Section 6.2, paragraph 2, to discusses this analyses in greater detail:

> Figure \ref{trigger_reg_graph} reports that the effect of moratoriums is more prominent when the corresponding trigger is a death or sexual assault rather than a behavior violation. In particular, alcohol offenses decline significantly when a fraternity-related death is the triggering event. To ensure that this is the result of the moratorium rather than the triggering death, I use an additional 15 universities that experienced a fraternity-related death in the sample period, but *did not* undergo a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities are those whose students experience the effect of a fraternity-related death, but do not experience a moratorium. First, I exclusively analyze these 15 non-moratorium universities by creating a 64-day binary treatment variable, beginning with the date of the death. A 64-day period is chosen as it is the average length of a moratorium. Next, I estimate the preferred specification using the 64-day period after the death in lieu of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by adding the 14 never-treated schools that are used in Section 5.3 as never-treated controls for the effect of a death. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related causes a decrease in alcohol or sexual assault offenses rather than the moratorium itself. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.










## Major Comment 2: Progression of a Moratorium

\begin{framed}
The author also suggests that the finding might inform administrators of the potential benefit of making a moratorium permanent. To address this question and to provide further evidence that the moratorium is causing the change and not the triggering event, I believe the author should also consider further examination of the variation in the length of the moratoriums. The author does explore the average daily effect of moratoriums across three lengths (Table 6). I was rather surprised to find the shortest moratoriums to have no effect (and a positive point estimate on alcohol offenses). Presumably none of these short moratoriums were due to a student death? As a reader, I was certainly left wondering if this was due to the type of triggering event. What I was hoping to see was an analysis that explicitly examined whether there are heterogenous impacts of the moratorium by how long it has been in effect. Over time, does the effect diminish within the moratorium? My understanding of the analysis is that the author explores different periods after the conclusion of a moratorium, but not different time periods within the moratorium. In Table 6, I don't know if the large negative impact on alcohol offenses are occurring evenly across the moratorium or primarily during the first 30 days. For policy implications, it would be incredibly valuable to understand when the reductions of alcohol offenses occur within the moratorium. This would inform both the optimal length of a moratorium and whether we would expect any benefit from a permanent ban on alcohol at these events.
\end{framed}

**Note that this is not my formal response yet, but an outline.**

I agree that this suggestion would be great for school administrators to more effectively plan their moratorium schedule. However, I have found that this is a challenging task given that each moratorium has a different length, and some schools can experience multiple moratoriums in the sample period. Therefore, given that the treatment period differs across and within schools, analyzing this clearly and effectively is quite difficult. As of now, I have formulated a table that gets at this in Appendix Figures \ref{alc_progression_g} and \ref{sex_progression_g}. What are your thoughts on this graph? I feel like it is very difficult to explain, hence why I deleted it from the paper initially.

## Major Comment 3: Update Table 7

\begin{framed}
To better interpret the results in Table 7, it would be helpful to know about the relative mean number of alcohol offenses at party schools versus non-party schools outside of a moratorium. It is possible for the reader to calculate this between the text in the second paragraph in section 6.1 and the information on Table 7, but it would be easier if it was provided. It would also highlight for the reader that party schools (as determined by the external rankings) do have more alcohol offenses per 25000 students than non-party schools.
\end{framed}

Thank you for this comment as it will certainly help readers better understand the amount of alcohol offenses/sexual assaults at party schools relative to non-party schools outside of a moratorium. I have added an additional paragraph in Section 6.1 to help highlight the fact that party schools have more alcohol offenses per 25000 students than non-party schools. I have included the paragraph below for convenience:

> As shown in Table \ref{party_school_table}, universities defined as party schools exhibit higher averages of alcohol offenses assaults relative to non-party schools. In particular, non-party schools experience approximately 49% less alcohol offenses on average. These differences are similar when excluding moratorium days (47%), although both party schools and non-party schools have relatively similar levels of sexual assaults.

\newpage

# Response to comments from Referee #4 \label{section:ref4}

## Major Suggestion 1: Leverage IFC Variation
\begin{framed}
Currently, the main specification treats all moratoriums the same. However, presumably a moratorium at a school with 1.3\% of the body in IFC fraternities is less impacted by a moratorium than one with 10.2\% IFC membership. Can you provide heterogeneity analysis that probes this difference in intensity of treatment? This could be accomplished by interacting moratorium with share IFC or looking at quartiles of share IFC etc. 
\end{framed}

Thank you for this thoughtful suggestion. I discuss this suggestion in the response to Referee #2, as they also had a similar recommendation. In summary, I have added a new section on this topic in Section 6.3 and added Table \ref{ifc_share} which shows the replacement of the $InMoratorium_{u,t}$ treatment variable in the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the most recent number of IFC fraternity members at university $u$, divided by the average total enrollment over the sample period. The main result shows that a 10% increase in the share of IFC members at a fraternity results in a 0.18 decrease in the number of alcohol offenses per-25000 enrolled students during a moratorium. This effect is statistically significant at the 5% level. Below I have added the text from the new Section 6.3 for convenience:

> In this subsection, I analyze whether universities with a higher fraction of their student body belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of their student population attributed to IFC fraternities. As shown in Table \ref{summary_stats}, the fraction of enrolled students belonging to an IFC fraternity can range from 1% to as high as 10%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

> To conduct this analysis, I replace the $InMoratorium_{u,t}$ treatment variable in the preferred specification with an interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$, where $FractionIFC_u$ is the most recent number of IFC fraternity members at university $u$, divided by the average total enrollment over the sample period. I use the most current count of IFC members since most universities do not hold semester-level records of this information. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations. Therefore, a recent one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a larger treatment than universities with lower shares.

> Table \ref{ifc_share} reports that universities with a higher fraction of their student enrollment belonging to an IFC fraternity exhibit larger decreases in alcohol offenses during a moratorium. In Column 1 of Panel A, the point estimate shows that a 10% increase in the share of IFC members at a fraternity results in a 0.18 decrease in the number of alcohol offenses per-25000 enrolled students during a moratorium. This effect is statistically significant at the 5% level, and, similar to the main results, is strongest on the weekends. In Panel B, although not statistically significant, the point estimates for sexual assaults follow a similar pattern as alcohol offenses—universities with a higher fraction of IFC members in their study body exhibit larger decreases of sexual assaults. Taken together, a moratorium affects students' alcohol-behavior more when the restrictions apply to a greater share of the student body.

Although not shown, I also explore analysis splitting the sample into quartiles based on the share of IFC members as you suggest. However, the relatively small number of universities in each quartile made the results weak, and statistically insignificant at the 10% level. This is the case for both alcohol offenses and sexual assaults. While I certainly agree that this analysis could be a great addition to the paper, the lack of power, insignificant results, and the concern of Referee #2 in whether this paper has strong enough results in general, lead me to include only the former analysis suggested.


## Major Suggestion 2: Separating Effect of Triggering Event \label{section:death_sug}

\begin{framed}
One interesting result is that impacts of moratoriums seem larger 
following a student death (Figure 8). This begs the question of whether the incident (death) 
changes behavior for a short time, or whether the moratorium changes behavior. I would like to 
see whether a death without a moratorium causes a change in alcohol and sexual assault 
violations. Can you test this hypothesis by considering the 64 days (avg moratorium length) after 
these deaths as treated? 
Note – this suggestion is distinct from the test conducted in Appendix C7. I want to know 
whether a death causes a treatment effect absent a moratorium. Your test in C7 shows a related 
but separate idea—that moratoriums still cause a treatment effect when compared to colleges that
have deaths but no moratoriums. Given that a large portion of the observations for a school with
only a death would still be considered “untreated” (days prior to the event or days after the 
treatment period ended) even if it had a moratorium, the test in C7 may be a weak test, and I 
would encourage you to use more conservative language in describing the results. 
\end{framed}

This is a fantastic suggestion that certainly strengths the paper. As requested, I estimate the main specification with the 15 universities that undergo a fraternity-related death but do not undergo a moratorium. I create a binary 64-day treatment variable that starts with the day of the death for each university. The results of this test are shown in Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest}. 

Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is no statistically significant effect when considering a 64-day period after a fraternity-related death. In Panel C of Appendix Figure \ref{alc_forest}, alcohol offenses show small, and positive point estimates, while in Panel C of Appendix Figure \ref{sex_forest}, sexual assaults show negative point estimates when considering all days of the week and on the weekdays. This provides evidence that the moratorium is producing the effects shown in the main results, rather than the triggering event itself. While moratoriums that are the result of a fraternity related death drive the results as discussed in Section 6.2, this may be due to students more-seriously abiding by the moratorium guidelines. 

Given the results and intuitive nature of this test, I believe that this analysis is better suited for the paper than the previous material I presented which utilized these 15 universities as simple never-treated control units. Therefore, I have omitted the old analysis in lieu of the new analysis shown in Appendix Figures \ref{alc_forest} and \ref{sex_forest}. Moreover, Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} also show an extension of this analysis by including a never-treated group as done in the robustness checks of Section 5.1. This inclusion of never-treated units is motivated by the relatively small number of clusters (15) in the initial analysis and is performed to increase precision. Although precision is minimally increased, the results remain consistent nonetheless.

Please note that Section 6.2 has now been updated to reflect the suggestions and subsequent analysis. What follows is the updated passage from Section 6.2, paragraph 2, which discusses this test and the results:

> Figure \ref{trigger_reg_graph} reports that the effect of moratoriums is more prominent when the corresponding trigger is a death or sexual assault rather than a behavior violation. In particular, alcohol offenses decline significantly when a fraternity-related death is the triggering event. To ensure that this is the result of the moratorium rather than the triggering death, I use an additional 15 universities that experienced a fraternity-related death in the sample period, but *did not* undergo a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities are those whose students experience the effect of a fraternity-related death, but do not experience a moratorium. First, I exclusively analyze these 15 non-moratorium universities by creating a 64-day binary treatment variable, beginning with the date of the death. A 64-day period is chosen as it is the average length of a moratorium. Next, I estimate the preferred specification using the 64-day period after the death in lieu of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by adding the 14 never-treated schools that are used in Section 5.3 as never-treated controls for the effect of a death. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related causes a decrease in alcohol or sexual assault offenses rather than the moratorium itself. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.


## Major Suggestion 3: Representativeness

\begin{framed}
It would be helpful to place the sample in context relative to the Greek-life ecosystem to comment about generalizability. For instance, what is a typical share IFC across all 4-year US colleges and universities and how does this differ from the sample? Some small private colleges have very large Greek presence in percentage terms (e.g. Depauw University is \~70\% Greek), but these schools are largely unrepresented in the sample. Would we expect results to generalize etc.? 
\end{framed}

I agree that there is not enough context surrounding the sample universities and how they relate to other universities in terms of Fraternity/Sorority Life. To give context surrounding the importance of fraternities at the sample universities relative to other schools, I use the Best Greek Life Colleges in America ranking from Niche.com. These rankings are based on survey responses from Niche.com users on the quality of Fraternity/Sorority Life at their school and 300 universities nation-wide are ranked. Furthermore, this list is used in Section 5.1 of the paper as criteria for adding never-treated universities.

Figure \ref{niche_ranking_graph} shows that the 37 universities in the sample are generally representative of schools with high-fraternity activity with the schools exhibiting a median ranking (represented by the dashed red line) of 64. In addition, 14 of the 37 universities (38%) are ranked in the top 50, while only 5 of 37 (13%) are not ranked. This figure has been added to the appendix as well as an additional sentence referring to the figure in Section 3.3 which reads "Although IFC members represent a small number of enrolled students, the universities in the sample are representative of schools with active Fraternity and Sorority Life (see Appendix Figure \ref{niche_ranking_graph})".

Unfortunately, there does not exist a data repository of IFC fraternity populations at the university level—the North American Interfraternity Conference (NIC) has informed me that they do not track such records. Moreover, the [US News Rankings of universities with the highest share of men in fraternities](https://www.usnews.com/best-colleges/rankings/most-frats), unfortunately, has two major shortcomings: first, it only reports percentages for 100 universities in the US, many of which are small universities. Second, and most importantly, the US News Rankings does not specify whether their statistics are based on strictly IFC fraternities. Recall from Section 2.1 that there are other types of fraternities such as academic, professional, and service fraternities. Although the statistics that I have for universities that are in both the list and sample match (for instance, I find Rollins College has 23% of their undergraduate male population as a member of an IFC fraternity, and the list finds 22%), I believe that using the Niche.com rankings provides better context given there is no ambiguity in how the rankings are determined.^[Please note that in the paper I report the fraction of total enrollment belonging to an IFC community rather than the fraction of undergraduate males which is why the maximum number I report in the summary statistics table is 10%.] 



\newpage
# References

<div id="refs"></div>


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/figures.Rmd", fig.pos="H"}

```


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/tables.Rmd", fig.pos = "H"}

```



\newpage
# Appendix {-}
```{=tex}
\appendix
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{A\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_twfe.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{B\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_spillover.Rmd", fig.pos='H' }

```

```{=tex}
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{C\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/appendix_figures.Rmd", fig.pos='H' }

```


