---
output: 
  pdf_document:
    number_sections: true
    extra_dependencies: ["flafter"]
indent: true
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage{bbm} ##for indicator
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage{framed}
- \usepackage{afterpage}
- \usepackage{geometry}
- \usepackage{indentfirst}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage{rotating}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\onehalfspacing
- \usepackage{subfig}
- \usepackage{placeins}
- \usepackage{fancyhdr}
- \pagestyle{fancy}
- \fancypagestyle{plain}{\pagestyle{fancy}}
- \fancyhead[R]{JHR Submission 0722-12422}
- \floatplacement{figure}{H}
- \setcounter{section}{-1}
linkcolor: blue
bibliography: "references.bib"
link-citations: yes
nocite: |
  @kaplandata, @ucrbook, @cameron_bootstrap-based_2008
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(tidyverse)
library(kableExtra)
library(bookdown)
library(modelsummary)
library(fixest)
library(grid)
library(gridExtra)
library(patchwork)
options(modelsummary_model_labels="model")
```

\noindent Thank you for the opportunity to revise and resubmit this journal submission. This revision contains updates which significantly strengthen the paper’s assumptions, results, and analyses. In this revision, the paper now contains a more convincing test to credibly argue that the effect of moratoriums is not driven by triggering events such as a death. In addition, weighted regressions are shown to verify the main results, moratorium dynamics are analyzed in the new Section 5.4, and heterogeneity analysis leveraging fraternity member population is newly discussed in Appendix \ref{asection:fraction}. Clarity has also been enhanced, as the paper now provides more context surrounding the sample universities, expands upon the missing details regarding the Campus Safety and Security Data, and more directly connects to the literature surrounding university policies and adolescent health. Despite these important additions, the length of the paper has grown minimally, as I have condensed the data collection/cleaning sections by over 500 words and moved minute details to the new Appendix \ref{asection:data}: Details on Data Collection. Please note that I have created sections and subsections to help organize this response. I provide all figures and tables at the end of this document so that they can be linked to my responses to the comments and suggestions. Section \ref{section:editor} responds to the suggestion from the editor. Section \ref{section:ref1} includes responses to all comments and suggestions provided by Referee #1, Section \ref{section:ref2} responds to comments and suggestions from Referee #2, Section \ref{section:ref3} responses to the report provided by Referee #3, and Section \ref{section:ref4} responds to suggestions from Referee #4. Note that all comments and suggestions from the referees are in boxes.

# Response to the Editor \label{section:editor}

## Suggestion for Improvement

\begin{framed}
\noindent Your analysis is a straight-up policy evaluation, which is fine and the JHR has published a number of papers of this type. Still, in their letters to me, all the reviewers raise the question whether this is an important enough question to warrant publication in the JHR. They fall on both sides of the divide, about equally split. R2 has perhaps the strongest concerns along those lines, which are outlined also in their comments to you. I believe it is an important question and goes to the core issue of whether university policies have any bite. However, the fact that all reviewers have the same concern signals to me that the importance of the question and the implications from your analysis could be emphasized more strongly and perhaps positioned in a somewhat wider literature.
\end{framed}

Thank you for your helpful insight on how to better phrase the core question of this paper. To emphasize the importance, I have more firmly placed the paper in a literature surrounding the effectiveness of university policies including academic probation, financial aid, and deferred recruitment—a fraternity/sorority-related policy. I now underscore the contrast between moratoriums and these policies, as moratoriums can be quickly implemented and distinctly alter a university’s social environment given that students unaffiliated with fraternities may still attend fraternity parties. In addition, I briefly describe two new findings in the introduction to address whether this university policy has any bite; first, that moratorium effects diminish after a month of implementation, and second, that there is suggestive evidence that schools with a higher share of fraternity life exhibit stronger moratorium effects. The added information improves the understanding of the results as it helps school administrators determine the appropriate duration of a moratorium, or whether a moratorium is even suitable given their fraternity-affiliated population. In addition, to position this paper in a somewhat broader literature, I have expanded the literature review to include a citation on the health effects of alcohol on adolescent brain development. By mentioning this, I hope to show readers that there could be implications beyond the decreases in alcohol offenses and sexual assaults that are explicitly analyzed in the paper. I have highlighted these points in the introduction, beginning in paragraph eight (page 3), which now reads:

> ...Second, this paper contributes to an emerging body of economic work relating to the effectiveness of university policy, and more specifically, fraternity policy. Although university policies such as academic probation [@lindo_alcohol_2013] and financial aid [@dynarski_does_2003] have been found to be effective in improving GPA and recruiting students respectively, there are only two studies as of this writing that analyze fraternity-targeted policies—both of which study the effects of deferring fraternity recruitment from freshman to sophomore year  [@de_donato_effects_2017;@even_greek_2020]. Moratoriums, in contrast, alter a university’s party culture instantly, since unaffiliated undergraduates also attend fraternity parties [@harford_attendance_2002]. However, as discussed in Section 5.4, the moratorium effects diminish following the first month of implementation, making them ill-suited as a long-term solution for mitigating excessive partying. Currently, only one related study has examined the relationship between fraternities and university crime [@raghav_greek_2021], although this study focuses on how the size of a fraternity population affects campus crime rather than the effect of a typical fraternity policy. I explore a similar idea in Appendix \ref{asection:fraction} which shows suggestive evidence that universities with higher shares of fraternity members exhibit larger moratorium effects...



# Response to comments from Referee #1 \label{section:ref1}

## Suggestion for Improvement
\begin{framed}

\noindent In the section about spillover analysis using Campus Safety and Security (CSS) data, the author has not specified if they used arrests for liquor law violations, disciplinary actions for liquor law violations, or some (weighted) average of both. Under Clery Act 1990, both the number of arrests and the number of disciplinary actions in residence halls (and elsewhere) are collected and reported by colleges and universities. However, the author has failed to specify which of the two they have used in this section of the paper. Not only should the author clearly specify which of these two variables is being used for the analysis in this section, but I would suggest that the author run separate analyses using each of the two variables (the number of arrests and disciplinary actions due to liquor law violations in residence halls) so that the reader can get some additional insights.
\end{framed}

This is an excellent suggestion as the delineation between disciplinary actions and arrests is important for interpretation, clarity, and replication purposes. In the reviewed draft, the Campus Safety and Security (CSS) analysis uses disciplinary actions for liquor law violations and excludes arrests. As suggested, I have extended the analysis to include both disciplinary actions and arrests for liquor law violations in Appendix \ref{asection:spillovers} and updated the final two paragraphs of Section 5.2 with additional commentary. Both of these extensions are further explained in the following paragraphs.

In Appendix Table \ref{css_arrests}, I delineate between disciplinary actions and arrests in the CSS data for alcohol offenses by adding Columns 4 and 5 which analyze the effect of moratoriums on arrests for all reports in the CSS and residence hall incidents respectively. Columns 4 and 5 show that there is little evidence of arrests changing at universities, regardless of the location. In particular, for each additional moratorium day in a calendar year, alcohol arrests per-25000 enrolled students do not exhibit any statistically significant decrease and the point estimates are relatively small when compared to disciplinary actions. This is consistent with the literature that campus police do not commonly arrest students for underage drinking [@bernat_college_2014]. Hence, while there is evidence that moratoriums affect student alcohol behavior, there is little evidence that moratoriums affect arrests for alcohol violations. In light of these findings, I have updated the final paragraph of Appendix \ref{asection:spillovers} to reflect this analysis:

> However, there is little evidence of an effect on liquor law arrests as shown in Columns 4 and 5—consistent with the literature that campus police do not typically arrest students for alcohol violations [@bernat_college_2014]. As discussed in Section 5.2, this supports the notion that if moratoriums displace alcohol-fueled behavior, they displace it to *less* risky areas whereby behavior can more easily be intervened before it becomes dangerous.

Given the lack of significance and small point estimates in the arrest columns, I update the final two paragraphs of Section 5.2 to address the delineation between arrests and disciplinary actions and save the additional analysis of arrests for Appendix \ref{asection:spillovers}. However, I am happy to move the analysis to the main paper upon the editor's request. The following is an excerpt from the updated Section 5.2 in the main paper:

> As the second set of analysis, I analyze the CSS data to examine if students substitute partying at fraternity houses to different on-campus locations during moratoriums. The CSS data contains all disciplinary actions and arrests corresponding to liquor law violations in addition to reports of sexual assaults that occur in a calendar-year...

\noindent The extension continues in the final paragraph where I more directly assert the findings:

> Using the CSS data, there is evidence that moratoriums move drinking from fraternity houses to residence halls. Residence halls show a 0.270 *increase* in yearly disciplinary actions of alcohol offenses for each additional moratorium day in a calendar-year. Interestingly, this is accompanied by a 0.033 *decrease* in yearly residence hall sexual assault reports.

Finally, the text of Appendix \ref{asection:spillovers} more closely describes the CSS data used and the corresponding results. As noted at the beginning of the document, the appendices are included at the end of this document for convenience.

\newpage

# Response to comments from Referee #2 \label{section:ref2}

## Suggestion #1: Weighting 

\begin{framed}
I'm not sure the results are strong enough. Qualitatively, the results are unsurprising - banning activities with involve alcohol will likely reduce crimes which involve alcohol. Quantitatively, the results are imprecise, and hence difficult to interpret confidently. The point estimates seem very large, alcohol related crimes reduced by 26\% despite the fraction of the students enrolled in IFC fraternities being less than 5\%. I'm not dismissing this magnitude as unfeasible - especially if the author could show some more supplementary evidence on the likely share of such crimes that are associated with fraternities. However, the CIs are wide, and do not rule out very small effects, so it is not clear whether or not the effects are actually 'large'. Of course these issues are true to a greater extent for the more imprecise results for sexual assault. 

Two suggestions which may improve precision: To weight by total enrollment (or perhaps undergraduate enrollment if you feel that is more appropriate). Larger schools should have less residual variation, so weighting by size should reduce standard errors. The variance in school size should be large enough for this to make a difference.
\end{framed}


Thank you for the thoughtful suggestion on how to tighten/strengthen the main results of the paper. First, I agree that despite the large point estimates, the standard errors do not rule out small effects. To reconcile this, I have deleted all language where I describe the effects as large. However, as pointed out, these estimates are not unfeasible. Although the data cannot delineate whether an incident is associated with fraternities, non-members are also likely affected by moratoriums as fraternity parties are a substantial source of partying for all undergraduates [@harford_attendance_2002]. Moreover, the magnitude (29% on weekends) for the decreases in sexual assaults are in-line with the increases (28%) found due to intensifying partying in @lindo_college_2018. 

Second, as recommended, I have explored weighting by total enrollment to tighten the main results. Unfortunately, the weights do not tighten the results to a significant degree. However, the results remain extremely consistent with their unweighted counterpart. For ease of comparison between the weighted and unweighted results, I have included a figure that is unique to this cover letter in Appendix Figure \ref{main_table_graphic_weighted}. In this figure, I show the point estimates and 95% confidence intervals for each specification (unweighted and weighted) from the main results table (Table \ref{main_table}). The figure demonstrates that the results are largely similar with minimal gains in precision across most specifications. However, to maintain transparency, I have included a table with the weighted main results in Table \ref{main_table_weighted}. In addition, I have also alluded to these weighted estimations when discussing the main results in paragraph three of Section 5.1 which reads: 

> Third, due to the large variation in university size, the models in Table \ref{main_table} are weighted by total enrollment in Appendix Table \ref{main_table_weighted}. The weighted estimations exhibit similar results to the unweighted models with alcohol offenses and sexual assaults decreasing by 29% and 32% on the weekends respectively, while the standard errors remain similar in magnitude.


## Suggestion #2: Leverage IFC Variation

\begin{framed}
To interact the treatment variable with the share of students who are in IFC fraternities. Perhaps I'm missing something, but I would expect the effect size to be essentially proportional to the proportion in IFC fraternities. To be clear, I'm suggesting replacing Moratorium (in equation 1) with Moratorium * Fraction\_IFC.
\end{framed}

This is a great suggestion, also proposed by Referee #4. Prompted by this, I have collected the additional data needed for this analysis as the data was previously missing four universities’ IFC population numbers. I have updated Section 6.1 with a short discussion and have added an additional Appendix \ref{asection:fraction} which more thoroughly describes the analysis. As discussed in the excerpts copied below, the results give suggestive evidence that higher proportions of IFC members at a university result in larger moratorium effects. However, these results are low powered with relatively large confidence intervals. To reconcile these results, I have conducted additional analysis which illuminate why these results are not as strong as intuition might suggest. I show that the IFC population numbers are a weak proxy for a school with an active fraternity/sorority life by plotting universities’ IFC fraction against their Niche.com Colleges with the Best Greek Life ranking. The following paragraphs describe both the recommended analysis, and the additional analysis.

First, as mentioned above, I have updated Section 6.1 with a short discussion on the results of the suggested analysis in paragraph four. This paragraph also links the reader to a more thorough discussion of this analysis in the new Appendix \ref{asection:fraction}. The contents of the new Appendix \ref{asection:fraction} are copied below:

> In this appendix, I analyze whether universities with a higher fraction of undergraduates belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of its student population belonging to IFC fraternities. Recall from Table \ref{summary_stats} that the fraction of undergraduate students with IFC membership can range from 1% to as high as 11%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

> To conduct this analysis, I supplement the preferred specification with an interaction of $InMoratorium_{u,t}$^[Note that I have changed the nomenclature of the main equation from reading $Moratorium_{u,t}$ to $InMoratorium_{u,t}$. This was done to align better with the tables/figures.] and $FractionIFC_u$, where $FractionIFC_u$ is the earliest recorded count of IFC fraternity members over 2014-2019 at university $u$, divided by the undergraduate enrollment, and centered at its mean. I use the earliest count of IFC members for two reasons; first, to avoid the potential issue of declines in IFC membership after a moratorium due to permanent suspensions of specific IFC chapters, and second, many universities do not maintain records of IFC numbers for every year in the sample period. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations.^[West Virginia University is an exception to this. Their official IFC count decreased by over 60 percent in years following the moratorium.] Therefore, an early one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a more intense treatment than universities with lower shares.

> Table \ref{ifc_share} provides suggestive evidence that moratoriums with a higher fraction of student enrollment belonging to an IFC fraternity result in larger decreases in alcohol offenses and sexual assaults during a moratorium period. In Panel A, the point estimates for the interaction term show patterns consistent with the main findings in the paper—the effects are negative with the strongest effects are observed on the weekends when partying is more frequent. Similarly, in Column 1 of Panel B, the interaction term coefficient shows suggestive evidence that moratoriums in universities with a higher share of IFC members exhibit larger decreases of sexual assaults. However, none of the interaction coefficients presented in either panel are significant, indicating only a suggestive relationship between the share of IFC members and the impact of moratoriums.

> The results of Table \ref{ifc_share} may appear surprisingly inconclusive given the expectation that universities with a higher share of fraternity members exhibit larger effects. One possible reason for these inconclusive results is that the share of fraternity members is a noisy indicator for a fraternity-related activity—schools with a small share of fraternity life may have chapters that are particularly active, or vice-versa. To demonstrate this, I plot each university’s undergraduate IFC fraction against its Niche.com Colleges with the Best Greek Life ranking. The ranking, based on survey responses from Niche.com users, ranges from 1-300, and 32 out of the 37 universities in the sample are ranked in the top 300. For the remaining five schools, I assign a ranking between 301-305. Figure \ref{scatter_rank_ifc} shows the inverse relationship between these two measures: as the Greek Life ranking increases, the fraction of undergraduates in an IFC fraternity generally decreases. This likely contributes to the negative point estimates in the previous analysis. However, this relationship is noisy, and the slope is not statistically different from zero at the 5% level. This may explain why the previous analysis only provided suggestive rather than clear evidence. 

Last, note that the Niche.com Colleges with Best Greek Life rankings list is similar to the Niche.com Top Party Schools in America list which I analyze in Section 6.1, Table \ref{party_school_table}. Specifically, 16 of the highest 18 ranked Greek Life universities in the sample are also defined as party schools. 


\newpage

# Response to comments from Referee #3 \label{section:ref3}

## Major Comment 1: Effect of a Death

\begin{framed}
In reading the manuscript, I was initially concerned that the author was not going to address the critical assumption that a triggering event that may lead to a moratorium does not also lead students to change their behavior in ways that would reduce alcohol offenses or sexual assaults - the outcomes of interest. It is plausible that the death of a peer as a result of risky behavior at a fraternity would lead students at the university to at least temporarily change their behavior in ways that would reduce alcohol offenses and sexual assaults. This concern would seem to merit discussion in section 4.2 "Identification Assumptions". While the author addresses the concern that the timing of fraternity moratoriums are as-good-as-random, it would seem equally important that the triggering event is not influencing both existence of a moratorium and the outcomes of interest. This analysis, that was critical for me to view the estimated effects as credibly causal, comes at the very end of the paper in section 6.2. This section "Does the Triggering Event for a Moratorium Matter?" primarily focuses on whether it matters if the triggering event is "...the result of a fraternity-related death, a prominent sexual assault, or a behavior violation." Finally, the author gets to the critical statement on page 24 "To ensure that this is the effect of the moratorium rather than the triggering death, Appendix Figure C7 shows the preferred specification restricted to only the universities that experienced a fraternity-related death with an additional 15 universities that experience a fraternity-related death in the same period, but did not undergo a moratorium." These additional universities and their experiences with a fraternity-related death but no moratorium provide a valuable comparison group. I believe the author needs to clarify the estimation equation used in this figure - I am assuming the author did what I would hope, but found the text and note in the figure less than clear. I also believe the author needs to put a greater spotlight on this issue and more clearly present the results, even if it weakens the findings. The results would still be important. However, as a college administrator considering a moratorium, I want to clearly understand the best estimate for how much I would be expected to reduce alcohol violations and sexual assaults by implementing a moratorium after a fraternity-related death of a student - beyond any expected reduction resulting from just the triggering event. The estimated impact of moratoriums on sexual assaults, in Figure C8, are not even explicitly mentioned in the text for this specification and sample.
\end{framed}

Thank you for the excellent comment. I agree that it is indeed plausible that the effect of a death—rather than the moratorium itself—could be contributing to the reductions in alcohol offenses that this paper shows and needs greater emphasis for the main results to be interpreted as causal. To address this concern, I make two major refinements in the paper. First, as suggested, I have highlighted this concern in Section 4.2 by including it as an additional assumption of the model (see page 12). I have also included a more detailed discussion of this assumption in paragraph 6 of Section 4.2, which directly responds to this concern.  Second, I conduct a new and more convincing test for showing that this assumption is plausible based on a suggestion from Referee #4. In this test, I utilize 15 universities that undergo a fraternity-related death during the sample period, but do not undergo a moratorium.  Using these 15 universities, I assign a 64-day treatment period starting with the date of the death and find little evidence that alcohol offenses or sexual assaults are affected by a fraternity-related death in the absence of a moratorium. This test is distinct from the previous test in the original draft that initially utilized these 15 universities as never-treated control units with the main sample and more directly tests the effect of a death without a moratorium. Considering the results of this stronger test, I have removed the old test, as this new analysis provides clearer evidence that the event of a death does not contribute to decreases found in the main results. To present these results, I have revised the Appendix Figures \ref{alc_forest} and \ref{sex_forest} to clearly convey the findings and distinguish between the samples.

Below, I have copied the updated Section 4.2 paragraph 6 which describes the added assumption and Section 6.2 paragraph 2 which tests this assumption for your convenience:

> (Section 4.2 paragraph 6: added assumption) To evaluate the third assumption that the triggering event is not changing student behavior, I perform heterogeneity analysis in Section 6.2 and analyze the effect of a moratorium by each triggering event. As discussed further in Section 6.2, I find that the main results are driven by moratoriums triggered by fraternity deaths. While it is plausible that the shock of a death, rather than a moratorium, contributes to behavior changes in students, I construct a sample of 15 universities that experience a fraternity-related death but no moratorium, and apply a 64-day treatment period (the average length of a moratorium) starting with the day of the death to test whether the shock of death alone affects student behavior. In doing so, I find little evidence that alcohol offenses or sexual assaults decrease due to the shock of a death—neither outcome shows a statistically significant decrease during the 64-day period following a death.  

> (Section 6.2 paragraph 2: testing of assumption) Figure \ref{trigger_reg_graph} reports that moratoriums have a stronger impact when triggered by a death or sexual assault, rather than a behavior violation. Specifically, alcohol offenses decrease notably when a fraternity-related death is the trigger. To confirm that this effect is caused by the moratorium rather than the triggering death, I analyze data from 15 additional universities that had a fraternity-related death in the sample period, but did not have a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities serve as a control group to observe the effect of a fraternity-related death without the influence of a moratorium. I exclusively analyze data from these 15 universities that did not have a moratorium by creating a 64-day binary treatment variable (i.e., the average length of a moratorium) beginning with the date of the death. Next, I estimate the preferred specification using the 64-day period after the death instead of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit statistically insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by including the 14 never-treated schools that are used in Section 5.3 as never-treated controls. This amounts to 29 universities, 15 of which undergo the effect of a death, and 14 of which receive no such treatment. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related death contributes to the decreases shown in alcohol and sexual assault offenses during a moratorium. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.



## Major Comment 2: Progression of a Moratorium

\begin{framed}
The author also suggests that the finding might inform administrators of the potential benefit of making a moratorium permanent. To address this question and to provide further evidence that the moratorium is causing the change and not the triggering event, I believe the author should also consider further examination of the variation in the length of the moratoriums. The author does explore the average daily effect of moratoriums across three lengths (Table 6). I was rather surprised to find the shortest moratoriums to have no effect (and a positive point estimate on alcohol offenses). Presumably none of these short moratoriums were due to a student death? As a reader, I was certainly left wondering if this was due to the type of triggering event. What I was hoping to see was an analysis that explicitly examined whether there are heterogenous impacts of the moratorium by how long it has been in effect. Over time, does the effect diminish within the moratorium? My understanding of the analysis is that the author explores different periods after the conclusion of a moratorium, but not different time periods within the moratorium. In Table 6, I don't know if the large negative impact on alcohol offenses are occurring evenly across the moratorium or primarily during the first 30 days. For policy implications, it would be incredibly valuable to understand when the reductions of alcohol offenses occur within the moratorium. This would inform both the optimal length of a moratorium and whether we would expect any benefit from a permanent ban on alcohol at these events.
\end{framed}

I agree that this suggestion gives valuable information for school administrators to more effectively plan their moratorium length. I have added an additional section, Section 5.4, which describes the analysis to address this suggestion. I have copied the contents of Section 5.4 below for convenience:

> Although moratoriums can reduce alcohol offenses, it is likely that the reductions are not consistent throughout the enforcement period. For instance, students may find alternative ways to party or enforcement may become less strict as the moratoriums continues. Therefore, it is crucial to understand both when and how long a moratorium is most effective, as this can aid school administrators in making informed decisions about future moratorium lengths. 

> To understand the progression of a moratorium's effectiveness, I split the $InMoratorium_{u,t}$ treatment variable into weekly bins for the first nine weeks of a moratorium and pool the remaining weeks into one bin (Moratorium Weeks 10+) as shown in Panel A of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}.^[Note that nine weeks is approximately the average length of a moratorium.] This amounts to 10 unique coefficients, each identifying the effect of the moratorium in the corresponding week. However, since moratorium lengths differ by university, each point estimate is identified by a different number of schools as shown in parenthesis on the x-axis. For example, the coefficient identifying the effect of a moratorium in Week 3 is identified by 33 universities that have a moratorium that reach the three-week length. Note that if a university has, for instance, a 22-day moratorium, this moratorium will contribute only one day to the identification of the Moratorium Week 4 coefficient.

> Panel A of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}, exhibit evidence that moratoriums are most effective in the first five weeks. In Panel A of Figure \ref{alc_passing_graph}, alcohol offenses show statistically significant declines at the 5% level in weeks one, two, and five of a moratorium. The effectiveness appears to trend upward after the fifth week, thereby suggesting that moratorium effectiveness may diminish over time. Similarly, sexual assaults show statistically significant declines in weeks one and three in Panel A of Figure \ref{sex_passing_graph}, while the effects appear to fade in later weeks.

> Although Panel A illustrates the by-week effect, it is possible that the significant declines in the first five weeks are driven by universities that have short moratoriums. To ensure that the trends are consistent across universities, I re-estimate the coefficients using only universities that have moratoriums longer than nine weeks in Panel B of Figures \ref{alc_passing_graph} and \ref{sex_passing_graph}. In each figure, Panel B shows similar trends to Panel A, although less precise due to the loss of power. The results suggest that long moratoriums exhibit the strongest effects during the initial weeks of implementation, and similarly, the effects diminish after approximately five weeks. 

## Major Comment 3: Update Table 7

\begin{framed}
To better interpret the results in Table 7, it would be helpful to know about the relative mean number of alcohol offenses at party schools versus non-party schools outside of a moratorium. It is possible for the reader to calculate this between the text in the second paragraph in section 6.1 and the information on Table 7, but it would be easier if it was provided. It would also highlight for the reader that party schools (as determined by the external rankings) do have more alcohol offenses per-25000 students than non-party schools.
\end{framed}

Thank you for this comment as it will certainly help readers better understand the level of alcohol offenses/sexual assaults at party schools relative to non-party schools outside of a moratorium. I have added an additional paragraph in Section 6.1 and have updated Table \ref{party_school_table} with the non-moratorium means to help highlight the fact that party schools have more alcohol offenses per 25000 students than non-party schools. I have included the paragraph below for convenience:

> As shown in Table \ref{party_school_table}, universities defined as party schools exhibit higher averages of alcohol offenses assaults relative to non-party schools. In particular, non-party schools experience approximately 49% less alcohol offenses on average. These differences are similar when excluding moratorium days (47%), although both party schools and non-party schools have relatively similar levels of sexual assaults.

\newpage

# Response to comments from Referee #4 \label{section:ref4}

## Major Suggestion 1: Leverage IFC Variation
\begin{framed}
Currently, the main specification treats all moratoriums the same. However, presumably a moratorium at a school with 1.3\% of the body in IFC fraternities is less impacted by a moratorium than one with 10.2\% IFC membership. Can you provide heterogeneity analysis that probes this difference in intensity of treatment? This could be accomplished by interacting moratorium with share IFC or looking at quartiles of share IFC etc. 
\end{framed}

Thank you for this thoughtful suggestion. Given that Referee #2 had the same suggestion, I copy my response in the following paragraphs for your convenience:


This is a great suggestion, also proposed by Referee #4. Prompted by this, I have collected the additional data needed for this analysis as the data was previously missing four universities’ IFC population numbers. I have updated Section 6.1 with a short discussion and have added an additional Appendix \ref{asection:fraction} which more thoroughly describes the analysis. As discussed in the excerpts copied below, the results give suggestive evidence that higher proportions of IFC members at a university result in larger moratorium effects. However, these results are low powered with relatively large confidence intervals. To reconcile these results, I have conducted additional analysis which illuminate why these results are not as strong as intuition might suggest. I show that the IFC population numbers are a weak proxy for a school with an active fraternity/sorority life by plotting universities’ IFC fraction against their Niche.com Colleges with the Best Greek Life ranking. The following paragraphs describe both the recommended analysis, and the additional analysis.

First, as mentioned above, I have updated Section 6.1 with a short discussion on the results of the suggested analysis in paragraph four. This paragraph also links the reader to a more thorough discussion of this analysis in the new Appendix \ref{asection:fraction}. The contents of the new Appendix \ref{asection:fraction} are copied below:

> In this appendix, I analyze whether universities with a higher fraction of undergraduates belonging to IFC fraternities exhibit larger effects during a moratorium. Each university in the sample has a different share of its student population belonging to IFC fraternities. Recall from Table \ref{summary_stats} that the fraction of undergraduate students with IFC membership can range from 1% to as high as 11%. Presumably, a moratorium has a greater effect on student behavior when the restrictions apply to a greater share of students.

> To conduct this analysis, I supplement the preferred specification with an interaction of $InMoratorium_{u,t}$^[Note that I have changed the nomenclature of the main equation from reading $Moratorium_{u,t}$ to $InMoratorium_{u,t}$. This was done to align better with the tables/figures.] and $FractionIFC_u$, where $FractionIFC_u$ is the earliest recorded count of IFC fraternity members over 2014-2019 at university $u$, divided by the undergraduate enrollment, and centered at its mean. I use the earliest count of IFC members for two reasons; first, to avoid the potential issue of declines in IFC membership after a moratorium due to permanent suspensions of specific IFC chapters, and second, many universities do not maintain records of IFC numbers for every year in the sample period. However, in the universities that do supply complete records, I do not find substantial semester-to-semester changes in IFC populations.^[West Virginia University is an exception to this. Their official IFC count decreased by over 60 percent in years following the moratorium.] Therefore, an early one-year measure of the IFC population is a good approximation for the other corresponding years. In effect, the interaction of $InMoratorium_{u,t}$ and $FractionIFC_u$ creates a measure of moratorium intensity—universities with a higher fraction of IFC members receive a more intense treatment than universities with lower shares.

> Table \ref{ifc_share} provides suggestive evidence that moratoriums with a higher fraction of student enrollment belonging to an IFC fraternity result in larger decreases in alcohol offenses and sexual assaults during a moratorium period. In Panel A, the point estimates for the interaction term show patterns consistent with the main findings in the paper—the effects are negative with the strongest effects are observed on the weekends when partying is more frequent. Similarly, in Column 1 of Panel B, the interaction term coefficient shows suggestive evidence that moratoriums in universities with a higher share of IFC members exhibit larger decreases of sexual assaults. However, none of the interaction coefficients presented in either panel are significant, indicating only a suggestive relationship between the share of IFC members and the impact of moratoriums.

> The results of Table \ref{ifc_share} may appear surprisingly inconclusive given the expectation that universities with a higher share of fraternity members exhibit larger effects. One possible reason for these inconclusive results is that the share of fraternity members is a noisy indicator for a fraternity-related activity—schools with a small share of fraternity life may have chapters that are particularly active, or vice-versa. To demonstrate this, I plot each university’s undergraduate IFC fraction against its Niche.com Colleges with the Best Greek Life ranking. The ranking, based on survey responses from Niche.com users, ranges from 1-300, and 32 out of the 37 universities in the sample are ranked in the top 300. For the remaining five schools, I assign a ranking between 301-305. Figure \ref{scatter_rank_ifc} shows the inverse relationship between these two measures: as the Greek Life ranking increases, the fraction of undergraduates in an IFC fraternity generally decreases. This likely contributes to the negative point estimates in the previous analysis. However, this relationship is noisy, and the slope is not statistically different from zero at the 5% level. This may explain why the previous analysis only provided suggestive rather than clear evidence. 

Last, note that the Niche.com Colleges with Best Greek Life rankings list is similar to the Niche.com Top Party Schools in America list which I analyze in Section 6.1, Table \ref{party_school_table}. Specifically, 16 of the highest 18 ranked Greek Life universities in the sample are also defined as party schools. 


## Major Suggestion 2: Separating Effect of Triggering Event \label{section:death_sug}

\begin{framed}
One interesting result is that impacts of moratoriums seem larger 
following a student death (Figure 8). This begs the question of whether the incident (death) changes behavior for a short time, or whether the moratorium changes behavior. I would like to see whether a death without a moratorium causes a change in alcohol and sexual assault violations. Can you test this hypothesis by considering the 64 days (avg moratorium length) after these deaths as treated? 
Note – this suggestion is distinct from the test conducted in Appendix C7. I want to know 
whether a death causes a treatment effect absent a moratorium. Your test in C7 shows a related but separate idea—that moratoriums still cause a treatment effect when compared to colleges that have deaths but no moratoriums. Given that a large portion of the observations for a school with only a death would still be considered “untreated” (days prior to the event or days after the treatment period ended) even if it had a moratorium, the test in C7 may be a weak test, and I would encourage you to use more conservative language in describing the results. 
\end{framed}

This is a very thoughtful suggestion that certainly strengthens the paper. As requested, I estimate the main specification using the 15 universities that undergo a fraternity-related death but do not undergo a moratorium. I create a binary 64-day treatment variable that starts with the day of the death for each university. The results of this test are shown in Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest}. Ultimately, there does not appear to be any evidence of a death-effect. I further describe this analysis in the proceeding paragraphs.  

Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is no statistically significant effect when considering a 64-day period after a fraternity-related death. In Panel C of Appendix Figure \ref{alc_forest}, alcohol offenses show small and positive point estimates, while in Panel C of Appendix Figure \ref{sex_forest}, sexual assaults show negative point estimates when including all days of the week or only weekdays. This provides evidence that the moratorium, rather than the triggering event, is driving the effects reported in the main results. While moratoriums that are triggered by a fraternity-related death drive the results as discussed in Section 6.2, this may be due to students taking the moratorium more seriously.

Given the results and intuitive nature of this test, I believe that this analysis is better suited for the paper than the previous material I presented which utilized these 15 universities as never-treated control units. As a result, I have omitted the old analysis and included the new analysis in Appendix Figures \ref{alc_forest} and \ref{sex_forest}. Moreover, Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} shows an extension of the above analysis by supplementing the 15 universities with the 14 never-treated groups that were used in a robustness check in Section 5.1. This inclusion of never-treated units is motivated by the relatively small number of clusters (15) in the initial analysis described above and is performed to increase precision. As reported in the figures, the addition of these 29 universities slightly increases precision, but the results remain consistent.

Please note that Section 6.2 has now been updated to reflect the suggestions and subsequent analysis. What follows is the updated passage from Section 6.2 paragraph 2, which discusses this test and the results:

> Figure \ref{trigger_reg_graph} reports that moratoriums have a stronger impact when triggered by a death or sexual assault, rather than a behavior violation. Specifically, alcohol offenses decrease notably when a fraternity-related death is the trigger. To confirm that this effect is caused by the moratorium rather than the triggering death, I analyze data from 15 additional universities that had a fraternity-related death in the sample period, but did not have a moratorium.^[These universities were found using Hank Nuwer's repository of hazing-related deaths in the US: https://www.hanknuwer.com/hazing-deaths/.] Hence, these supplemental universities serve as a control group to observe the effect of a fraternity-related death without the influence of a moratorium. I exclusively analyze data from these 15 universities that did not have a moratorium by creating a 64-day binary treatment variable (i.e., the average length of a moratorium) beginning with the date of the death. Next, I estimate the preferred specification using the 64-day period after the death instead of the $InMoratorium_{u,t}$ treatment variable. Panel C of Appendix Figures \ref{alc_forest} and \ref{sex_forest} show that there is little evidence of declines in alcohol offenses or sexual assaults following a fraternity-related death without a moratorium. The point estimates for alcohol offenses are consistently positive, while both offenses exhibit statistically insignificant estimates at the 10% level. To increase precision, I supplement this analysis in Panel D of Appendix Figures \ref{alc_forest} and \ref{sex_forest} by including the 14 never-treated schools that are used in Section 5.3 as never-treated controls. This amounts to 29 universities, 15 of which undergo the effect of a death, and 14 of which receive no such treatment. As shown, the point estimates remain consistent across both of these analyses and the statistical significance does not change. Taken together, there is little evidence suggesting that a fraternity-related death contributes to the decreases shown in alcohol and sexual assault offenses during a moratorium. Instead, this points to the possibility that students may more seriously abide by the moratorium guidelines when the triggering event is a death.


## Major Suggestion 3: Representativeness

\begin{framed}
It would be helpful to place the sample in context relative to the Greek-life ecosystem to comment about generalizability. For instance, what is a typical share IFC across all 4-year US colleges and universities and how does this differ from the sample? Some small private colleges have very large Greek presence in percentage terms (e.g. Depauw University is \~70\% Greek), but these schools are largely unrepresented in the sample. Would we expect results to generalize etc.? 
\end{framed}

I certainly agree that there is not enough context surrounding the sample universities and their relation to other universities in terms of Fraternity/Sorority Life. Unfortunately, a data repository of IFC fraternity populations at the university level is not available; the North American Interfraternity Conference (NIC) has informed me that they do not keep such records. Moreover, the [US News Rankings of universities with the highest share of men in fraternities](https://www.usnews.com/best-colleges/rankings/most-frats), has two major shortcomings. First, it only reports fraternity membership percentages for 100 universities in the US, many of which are small. Second, and more importantly, the US News Rankings does not specify whether their statistics are based on strictly IFC fraternities. As mentioned in Section 2.1, there are other types of fraternities such as academic, professional, and service fraternities. Although the statistics that I have collected for universities that are in both the list and in the sample coincide (for instance, I find Rollins College has 23% of their undergraduate male population as a member of an IFC fraternity, and the list finds 22%), I would prefer to be cautious about this source of data given its lack of clarity.^[Please note that in the paper I report the fraction of undergraduate enrollment belonging to an IFC community rather than the fraction of undergraduate males which is why the maximum number I report in the summary statistics table is 11%.] 

As an alternative way to give context surrounding the importance of fraternities at the sample universities relative to other schools, I use the Best Greek Life Colleges in America ranking from Niche.com. These rankings are based on survey responses from Niche.com users on the quality of Fraternity/Sorority Life at their school and 300 universities nation-wide are ranked. Furthermore, this list is used in Section 5.1 of the paper as criteria for adding never-treated universities.

Figure \ref{niche_ranking_graph} shows that the 37 universities in the sample are generally representative of schools with high-fraternity activity with the schools exhibiting a median ranking (represented by the dashed red line) of 64. In addition, 14 of the 37 universities (38%) are ranked in the top 50, while only 5 of 37 (13%) are not ranked. This figure has been added to the appendix as well as an additional sentence referring to the figure in Section 3.3 which reads, "Although IFC members represent a small number of enrolled students, the universities in the sample are representative of schools with active Fraternity and Sorority Life (see Appendix Figure \ref{niche_ranking_graph})".

## Minor Suggestion 1: Condensing Sections 3.1 and 3.2
\begin{framed}
Sections 3.1 and 3.2 could be condensed with some of the material moved to the online appendix.
\end{framed}

Thank you for this suggestion to add conciseness to the paper. As recommended, I have shortened Sections 3.1 and 3.2 by approximately 500 words and moved extraneous details to a newly created Appendix \ref{asection:data}. This has reduced the length of these sections from four pages to two. 


\newpage
# References

<div id="refs"></div>


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/figures.Rmd", fig.pos="H"}

```


\newpage
```{r, child = "paper_iterations/working_paper_november_2022/tables.Rmd", fig.pos = "H"}

```



\newpage
# Appendix {-}

```{=tex}
\appendix
\renewcommand{\thefigure}{A\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{A\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{A\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_data_referee.Rmd", fig.pos='H' }

```

\newpage

```{=tex}

\renewcommand{\thefigure}{B\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{B\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{B\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_twfe_referee.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{C\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{C\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{C\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_spillover_referee.Rmd", fig.pos='H' }

```


\newpage
```{=tex}
\renewcommand{\thefigure}{D\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{D\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{D\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```

```{r, child = "paper_iterations/working_paper_november_2022/appendix_fraction_ifc.Rmd", fig.pos='H' }

```




\newpage
```{=tex}
\renewcommand{\thefigure}{E\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{E\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{E\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```
```{r, child = "paper_iterations/working_paper_november_2022/appendix_figures.Rmd", fig.pos='H' }

```


\newpage

```{=tex}
\renewcommand{\thefigure}{F\arabic{figure}} \setcounter{figure}{0}
\renewcommand{\thetable}{F\arabic{table}} \setcounter{table}{0}
\renewcommand{\theequation}{F\arabic{table}} \setcounter{equation}{0}
\setcounter{page}{1}
```
```{r, child = "paper_iterations/working_paper_november_2022/referee_figures.Rmd", fig.pos='H' }

```

