---
title: "Tables for Kevin: Baseline Specification"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning= F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
library(kableExtra)
library(tidyverse)
library(lubridate)
library(modelsummary)
library(maps)
theme_set(theme_minimal())
```

```{r}
source("figures/regressions_semesters.R")
```

# Tables

Here are the tables. For "semester before" there is an indicator variable equal to 1 if the semester is the semester before a moratorium starts. For "semester after" there is an indicator variable equal to 1 if the semester is the semester following the end of a moratorium.

Table \ref{alc_offense} shows the table of alcohol offenses aggregated to the semester level with two types of fixed effects specifications.  

Table \ref{drug_offense} shows the table of drug offenses aggregated to the semester level with two types of fixed effects specifications.

Table \ref{sex_offense} shows the table of sexual assault offenses aggregated to the semester level with two types of fixed effects specifications.


```{r}
alc %>% 
  landscape()
```

```{r}
drug %>% 
  landscape()
```

```{r}
sex %>% 
  landscape()
```

