---
title: "New Tables"
author: 
  - Michael Topper
date: "Last Updated: `r Sys.Date()`"
output: 
  pdf_document:
    number_sections: true
    citation_package: natbib
    # latex_engine: xelatex # If i hashtag it out my code works? I'm not sure
indent: true
header-includes:
- \usepackage{amsfonts}
- \usepackage{amsthm}
- \usepackage{amsmath}
- \usepackage[english]{babel}
- \usepackage{bm}
- \usepackage{float}
- \usepackage[fontsize=12pt]{scrextend}
- \usepackage{graphicx}
- \usepackage{indentfirst}
- \usepackage[utf8]{inputenc}
- \usepackage{pdfpages}
- \usepackage[round,authoryear]{natbib}
- \usepackage{setspace}\doublespacing
- \usepackage{subfig}
- \theoremstyle{definition}
- \newtheorem{definition}{Definition}[section]
- \newtheorem{assumption}{Assumption}
- \newtheorem{theorem}{Theorem}[section]
- \newtheorem{corollary}{Corollary}[theorem]
- \newtheorem{lemma}[theorem]{Lemma}
- \newtheorem*{remark}{Remark}
- \newcommand{\magenta}[1]{\textcolor{magenta}{#1}}
- \newcommand{\indep}{\perp \!\!\! \perp}
- \floatplacement{figure}{H}
- \usepackage{natbib}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r}
library(kableExtra)
source("figures/regressions_semesters.R")
source("figures/regression_semester_pois.R")
```



# Results from Aggregating

I aggregated everything to the semester level. I estimated two separate models. The first labeled (1) is with university and semester-by-year fixed effects. The second labeled (2) is with university-by-semester-number (e.g. univeresity interacted with either spring or fall semester) and a year fixed effect.

I estimated this two separate ways: one with OLS and one with Poisson. I don't think these look as robust as the other results, but at least the effects are still there and seem to be in line in magnitude to the other effects I saw with the other models.

Lastly, I did a decomposition for model (1) using the DeChaismartin decomposition for negative weights. In this case, the TWFE estimator estimates a weighted sum of 64 ATTs where 55 of the ATTs receive positive weight and 9 receive negative weight. The sum of the positive weights is 1.01 while the sum of the negative weights is -.01. This TWFE estimator is compatible with a DGP where those ATT all are of a different sign than beta.


Alcohol offenses are shown in Tables \ref{alc_offense} and \ref{alc_offense_p}. Drug offenses are shown in Tables \ref{drug_offense} and \ref{drug_offense_p}. Sexual assaults are shown in Tables \ref{sex_offense_p}.

```{r}
alc %>% 
  landscape()
```

```{r}
alc_p %>% 
  landscape()
```

```{r}
drug %>% 
  landscape()
```

```{r}
drug_p %>% 
  landscape()
```

```{r}
sex %>% 
  landscape()
```

```{r}
sex_p %>% 
  landscape()
```






