---
title: "Tables"
output: pdf_document
bibliography: references.bib
linkcolor: blue
editor_options: 
  chunk_output_type: console
header-includes:
- \usepackage{subfig}
---


<!-- ```{r setup, include=FALSE} -->
<!-- ## get rid of this entire chunk before knitting -->
<!-- knitr::opts_chunk$set(echo = F, message = F, warning= F) -->
<!-- knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) -->
<!-- library(kableExtra) -->
<!-- library(tidyverse) -->
<!-- library(lubridate) -->
<!-- library(modelsummary) -->
<!-- theme_set(theme_minimal()) -->
<!-- ``` -->



# Tables


```{r}
source(paste0(here::here("Tables/matching_word_table.R")))
```

```{r matching_table}
kable(matching_table, booktabs = T, caption = "Words/phrases used to pattern match on outcomes of interest.") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T, color = "blue") %>%
  column_spec(2, width = "20em") %>% kable_styling(latex_options = "HOLD_position")
```

\begin{landscape}
```{r top_categories}
kable(top_categories, booktabs = T, caption = "The top 30 most frequent reported incidents after pattern matching into each category. Numbers in parenthesis denote the frequency of offense in the data.") %>%
  kable_styling(latex_options = "scale_down")
```
\end{landscape}

```{r}
source(paste0(here::here("Tables/closure_table.R")))
```

```{r closure_table}
options(knitr.kable.NA = '')
kbl(closure_table, booktabs = T, caption = "All universities included in the sample and their respective moratorium dates.", col.names = c("University", "Moratorium 1 Start", "Moratorium 1 End",
                                                                                                                                           "Moratorium 2 Start", "Moratorium 2 End")) %>%
  kable_styling(latex_options = "scale_down")


```

```{r summarystatscrime}
source(paste0(here::here("Tables/summary_stats_offenses.R")))
```

```{r }
summary_stats_crime
```

```{r university_characteristics}
source(paste0(here::here("Tables/summary_stats_university.R")))
```

```{r}
university_characteristics
```

```{r lag_regressions}
source(paste0(here::here("Figures/lag_regressions.R")))
```

```{r}
lag_regresion_table
```





<!-- ```{r main_results} -->
<!-- source(paste0(here::here("Figures/regression_main_table.R"))) -->
<!-- ``` -->
\begin{landscape}
\begin{table}

\caption{\label{main_ols_alc}Effect of Moratoriums on Alcohol Offenses.}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Full Sample (Monday - Sunday)}}\\
\hspace{1em}Moratorium & -0.141** & -0.143** & -0.141** & -0.141**\\
\hspace{1em} & (0.050) & (0.049) & (0.047) & (0.047)\\
\hspace{1em}Num.Obs. & 56614 & 56614 & 56614 & 56614\\
\hspace{1em}Mean of Dependent Variable & 0.500 & 0.500 & 0.500 & 0.500\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekends (Friday - Sunday)}}\\
\hspace{1em}Moratorium & -0.320** & -0.328** & -0.277** & -0.276**\\
\hspace{1em} & (0.108) & (0.107) & (0.098) & (0.099)\\
\hspace{1em}Num.Obs. & 24287 & 24287 & 24287 & 24287\\
\hspace{1em}Mean of Dependent Variable & 0.890 & 0.890 & 0.890 & 0.890\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekdays (Monday - Thursday)}}\\
\hspace{1em}Moratorium & -0.008 & -0.003 & -0.040 & -0.040\\
\hspace{1em} & (0.024) & (0.027) & (0.034) & (0.034)\\
\hspace{1em}Num.Obs. & 32327 & 32327 & 32327 & 32327\\
\hspace{1em}Mean of Dependent Variable & 0.207 & 0.207 & 0.207 & 0.207\\
\midrule
Std. Errors & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university)\\
FE: day\_of\_week & X & X & X & X\\
FE: semester\_number &  & X &  & \\
FE: university & X & X &  & \\
FE: university\_by\_semester\_number &  &  & X & \\
FE: university\_by\_year\_by\_semester\_number &  &  &  & X\\
FE: year & X & X & X & \\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\textsuperscript{} The sample includes 38 universities. Some universities go in and out of moratoriums multiple times.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered by university.}\\
\multicolumn{5}{l}{\textsuperscript{} Outcome of interest is alcohol offenses per 25 thousand students.}\\
\multicolumn{5}{l}{\textsuperscript{} Coefficient estimates shown are for Moratorium.}\\
\multicolumn{5}{l}{\textsuperscript{} Full Sample includes only academic calendar days (plus 1 extra week on each end).}\\
\end{tabular}
\end{table}

\begin{table}

\caption{\label{main_ols_sex}Effect of Moratoriums on Reports of Sexual Assualt}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Full Sample (Monday - Sunday)}}\\
\hspace{1em}Moratorium & -0.011+ & -0.009+ & -0.005 & -0.005\\
\hspace{1em} & (0.006) & (0.005) & (0.007) & (0.007)\\
\hspace{1em}Num.Obs. & 56614 & 56614 & 56614 & 56614\\
\hspace{1em}Mean of Dependent Variable & 0.500 & 0.500 & 0.500 & 0.500\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekends (Friday - Sunday)}}\\
\hspace{1em}Moratorium & -0.014* & -0.012+ & -0.017+ & -0.017+\\
\hspace{1em} & (0.006) & (0.006) & (0.009) & (0.009)\\
\hspace{1em}Num.Obs. & 24287 & 24287 & 24287 & 24287\\
\hspace{1em}Mean of Dependent Variable & 0.890 & 0.890 & 0.890 & 0.890\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekdays (Monday - Thursday)}}\\
\hspace{1em}Moratorium & -0.008 & -0.007 & 0.004 & 0.004\\
\hspace{1em} & (0.008) & (0.007) & (0.009) & (0.009)\\
\hspace{1em}Num.Obs. & 32327 & 32327 & 32327 & 32327\\
\hspace{1em}Mean of Dependent Variable & 0.207 & 0.207 & 0.207 & 0.207\\
\midrule
Std. Errors & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university)\\
FE: day\_of\_week & X & X & X & X\\
FE: semester\_number &  & X &  & \\
FE: university & X & X &  & \\
FE: university\_by\_semester\_number &  &  & X & \\
FE: university\_by\_year\_by\_semester\_number &  &  &  & X\\
FE: year & X & X & X & \\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\textsuperscript{} The sample includes 38 universities. Some universities go in and out of moratoriums multiple times}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered by university.}\\
\multicolumn{5}{l}{\textsuperscript{} Outcome of interest is alcohol offenses per 25 thousand students.}\\
\multicolumn{5}{l}{\textsuperscript{} Coefficient estimates shown are for Moratorium.}\\
\multicolumn{5}{l}{\textsuperscript{} Full Sample includes only academic calendar days (plus 1 extra week on each end).}\\
\end{tabular}
\end{table}
\end{landscape}


\begin{landscape}
\begin{table}

\caption{\label{main_ols}Effect of Moratoriums on Alcohol Offenses and Sexual Assault (OLS).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Alcohol Offense} & \multicolumn{4}{c}{Sexual Assault} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & (1) & (2) & (3) & (4) & (1)  & (2)  & (3)  & (4) \\
\midrule
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Full Sample (Monday - Sunday)}}\\
\hspace{1em}Moratorium & -0.141** & -0.143** & -0.141** & -0.141** & -0.011+ & -0.009+ & -0.005 & -0.005\\
\hspace{1em} & (0.050) & (0.049) & (0.047) & (0.047) & (0.006) & (0.005) & (0.007) & (0.007)\\
\hspace{1em}Num.Obs. & 56614 & 56614 & 56614 & 56614 & 56614 & 56614 & 56614 & 56614\\
\hspace{1em}Mean of Dependent Variable & 0.500 & 0.500 & 0.500 & 0.500 & 0.057 & 0.057 & 0.057 & 0.057\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Weekends (Friday - Sunday)}}\\
\hspace{1em}Moratorium & -0.320** & -0.328** & -0.277** & -0.276** & -0.014* & -0.012+ & -0.017+ & -0.017+\\
\hspace{1em} & (0.108) & (0.107) & (0.098) & (0.099) & (0.006) & (0.006) & (0.009) & (0.009)\\
\hspace{1em}Num.Obs. & 24287 & 24287 & 24287 & 24287 & 24287 & 24287 & 24287 & 24287\\
\hspace{1em}Mean of Dependent Variable & 0.890 & 0.890 & 0.890 & 0.890 & 0.052 & 0.052 & 0.052 & 0.052\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Weekdays (Monday - Thursday)}}\\
\hspace{1em}Moratorium & -0.008 & -0.003 & -0.040 & -0.040 & -0.008 & -0.007 & 0.004 & 0.004\\
\hspace{1em} & (0.024) & (0.027) & (0.034) & (0.034) & (0.008) & (0.007) & (0.009) & (0.009)\\
\hspace{1em}Num.Obs. & 32327 & 32327 & 32327 & 32327 & 32327 & 32327 & 32327 & 32327\\
\hspace{1em}Mean of Dependent Variable & 0.207 & 0.207 & 0.207 & 0.207 & 0.061 & 0.061 & 0.061 & 0.061\\
\midrule
Std. Errors & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university)\\
FE: day\_of\_week & X & X & X & X & X & X & X & X\\
FE: semester\_number &  & X &  &  &  & X &  & \\
FE: university & X & X &  &  & X & X &  & \\
FE: university\_by\_semester\_number &  &  & X &  &  &  & X & \\
FE: university\_by\_year\_by\_semester\_number &  &  &  & X &  &  &  & X\\
FE: year & X & X & X &  & X & X & X & \\
\bottomrule
\multicolumn{9}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{9}{l}{\textsuperscript{} The sample includes 38 universities. Some universities go in and out of moratoriums multiple times.}\\
\multicolumn{9}{l}{\textsuperscript{} Standard errors are clustered by university.}\\
\multicolumn{9}{l}{\textsuperscript{} Outcomes of interest are alcohol offenses and reports of sexual assaults per 25 thousand students.}\\
\multicolumn{9}{l}{\textsuperscript{} Coefficient estimates shown are for Moratorium.}\\
\end{tabular}}
\end{table}
\end{landscape}




\begin{landscape}
\begin{table}

\caption{\label{main_pois}Effect of Moratoriums on Alcohol Offenses and Sexual Assault (Poisson).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lcccccccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{4}{c}{Alcohol Offense} & \multicolumn{4}{c}{Sexual Assault} \\
\cmidrule(l{3pt}r{3pt}){2-5} \cmidrule(l{3pt}r{3pt}){6-9}
  & (1) & (2) & (3) & (4) & (1)  & (2)  & (3)  & (4) \\
\midrule
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Full Sample (Monday - Sunday)}}\\
\hspace{1em}Moratorium & -0.243* & -0.217* & -0.343*** & -0.343*** & -0.181+ & -0.159+ & -0.170 & -0.170\\
\hspace{1em} & (0.102) & (0.094) & (0.100) & (0.100) & (0.100) & (0.094) & (0.120) & (0.120)\\
\hspace{1em}Num.Obs. & 56614 & 56614 & 53920 & 53866 & 56614 & 56614 & 51656 & 51586\\
\hspace{1em}Mean of Dependent Variable & 0.537 & 0.537 & 0.537 & 0.537 & 0.057 & 0.057 & 0.057 & 0.057\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Weekends (Friday - Sunday)}}\\
\hspace{1em}Moratorium & -0.320** & -0.296** & -0.413*** & -0.412*** & -0.221+ & -0.211 & -0.345+ & -0.345+\\
\hspace{1em} & (0.106) & (0.097) & (0.106) & (0.106) & (0.127) & (0.135) & (0.193) & (0.193)\\
\hspace{1em}Num.Obs. & 23625 & 23625 & 22568 & 22540 & 24287 & 24287 & 19759 & 19726\\
\hspace{1em}Mean of Dependent Variable & 0.957 & 0.957 & 0.957 & 0.957 & 0.053 & 0.053 & 0.053 & 0.053\\
\addlinespace[0.3em]
\multicolumn{9}{l}{\textbf{Weekdays (Monday - Thursday)}}\\
\hspace{1em}Moratorium & -0.030 & -0.000 & -0.157 & -0.157 & -0.155 & -0.126 & -0.049 & -0.049\\
\hspace{1em} & (0.111) & (0.117) & (0.162) & (0.162) & (0.123) & (0.115) & (0.145) & (0.145)\\
\hspace{1em}Num.Obs. & 32327 & 32327 & 29362 & 29331 & 32327 & 32327 & 27527 & 27494\\
\hspace{1em}Mean of Dependent Variable & 0.222 & 0.222 & 0.222 & 0.222 & 0.060 & 0.060 & 0.060 & 0.060\\
\midrule
Std. Errors & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (university)\\
FE: day\_of\_week & X & X & X & X & X & X & X & X\\
FE: semester\_number &  & X &  &  &  & X &  & \\
FE: university & X & X &  &  & X & X &  & \\
FE: university\_by\_semester\_number &  &  & X &  &  &  & X & \\
FE: university\_by\_year\_by\_semester\_number &  &  &  & X &  &  &  & X\\
FE: year & X & X & X &  & X & X & X & \\
\bottomrule
\multicolumn{9}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{9}{l}{\textsuperscript{} The sample includes 38 universities. Some universities go in and out of moratoriums multiple times.}\\
\multicolumn{9}{l}{\textsuperscript{} Standard errors are clustered by university.}\\
\multicolumn{9}{l}{\textsuperscript{} Outcomes of interest are alcohol offenses and reports of sexual assault counts.}\\
\multicolumn{9}{l}{\textsuperscript{} Coefficient estimates shown are for Moratorium.}\\
\end{tabular}}
\end{table}
\end{landscape}

```{r robbery}
## might want to redo this if you have some time and just put in all the other regressions
source(paste0(here::here("Figures/other_outcomes_regressions.R")))
```

```{r}
## insert newtable
other_outcomes_table
```




```{r hetero_trigger_alc}
source(paste0(here::here("Figures/heteroeffects_trigger_alc.R")))
```


```{r}
heteroeffects_alc %>%
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```


```{r hetero_trigger_sex}
source(paste0(here::here("Figures/heteroeffects_trigger_sex.R")))
```


```{r}
heteroeffects_sex %>%
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```



```{r hetero_uni_ifc}
source(paste0(here::here("Figures/heteroeffects_uni_ifc.R")))
```

```{r}
uni_enacted_alc %>%
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```


```{r}
source(here::here("Figures/clery_regressions.R"))
```

```{r}
clery_reg_table %>% 
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```

```{r}
source(here::here("Figures/nibrs_regressions.R"))
```

```{r}
nibrs_schools_table %>%
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```

```{r}
nibrs_all_table %>%
  landscape() %>%
  kable_styling(latex_options = "scale_down")
```


\begin{landscape}
\begin{table}

\caption{\label{death_regression}Effect of Moratoriums on Alcohol Offenses for Universities with Fraternity Deaths Only.}
\centering
\begin{tabular}[t]{lcccc}
\toprule
  & (1) & (2) & (3) & (4)\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Full Sample (Monday - Sunday)}}\\
\hspace{1em}Moratorium & -0.163 & -0.163 & -0.210+ & -0.210+\\
\hspace{1em} & (0.115) & (0.115) & (0.100) & (0.105)\\
\hspace{1em}Num.Obs. & 15044 & 15044 & 15044 & 15044\\
\hspace{1em}Mean of Dependent Variable & 0.674 & 0.674 & 0.674 & 0.674\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekends (Friday - Sunday)}}\\
\hspace{1em}Moratorium & -0.389 & -0.404 & -0.405+ & -0.405+\\
\hspace{1em} & (0.227) & (0.222) & (0.219) & (0.219)\\
\hspace{1em}Num.Obs. & 6453 & 6453 & 6453 & 6453\\
\hspace{1em}Mean of Dependent Variable & 1.198 & 1.198 & 1.198 & 1.198\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Weekdays (Monday - Thursday)}}\\
\hspace{1em}Moratorium & 0.015 & 0.021 & -0.055 & -0.055\\
\hspace{1em} & (0.048) & (0.060) & (0.057) & (0.057)\\
\hspace{1em}Num.Obs. & 8591 & 8591 & 8591 & 8591\\
\hspace{1em}Mean of Dependent Variable & 0.279 & 0.279 & 0.279 & 0.279\\
\midrule
Std. Errors & Clustered (university) & Clustered (university) & Clustered (university) & Clustered (day\_of\_week)\\
FE: day\_of\_week & X & X & X & X\\
FE: university & X & X &  & \\
FE: university\_by\_semester\_number &  &  & X & \\
FE: university\_by\_year\_by\_semester\_number &  &  &  & X\\
FE: year & X & X & X & \\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} + p $<$ 0.1, * p $<$ 0.05, ** p $<$ 0.01, *** p $<$ 0.001}\\
\multicolumn{5}{l}{\textsuperscript{} The sample includes 25 universities. 10 universities undergo moratoriums, while 15 do not.}\\
\multicolumn{5}{l}{\textsuperscript{} The 15 untreated universities experienced a fraternity-related death but no moratorium.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered by university.}\\
\multicolumn{5}{l}{\textsuperscript{} Outcome of interest is alcohol offenses per 25 thousand students.}\\
\multicolumn{5}{l}{\textsuperscript{} Coefficient estimates shown are for Moratorium.}\\
\multicolumn{5}{l}{\textsuperscript{} Full Sample includes only academic calendar days (plus 1 extra week on each end).}\\
\end{tabular}
\end{table}
\end{landscape}



