---
title: "Untitled"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(fixest)
library(lubridate)
library(modelsummary)
```

```{r}
source(here::here("Figures/event_study_multiple.R"))
source(here::here("Figures/event_study_weekdays.R"))
source(here::here("Figures/event_study_weekends.R"))
```

# New changes to the model

I decided to change the model a little bit after presenting in reading group. A big fear a lot of people have were that there were lasting effects of a moratorium, which the model does not account for. My previous model assumed that all effects were instantaneous - fraternities stop partying immediately and begin partying immediately following a moratorium and lifting of a moratorium respectively. To combat this, I decided to add in a "week before" and a "week after" control. Each of these controls are indicators equal to 1 for each 7 day period before and following a moratorium. If the effects of this policy is truly instantaneous, I would expect to see dips during treatment, and nulls elsewhere. Results are shown below:




# Event Studies with preferred specification

Want to produce several event studies. All of these are aggregated up to the weekly level. No further manipulations are used. The time fixed effects are university-by-semester-number.

```{r}
es_alc_graph
es_sex_graph
es_drug_graph
es_theft_graph
```

## Weekends

The following are subsetted from the sample above to only include Friday-Sunday. Fixed effects remain the same.

```{r}
es_alc_weekends_graph
es_sex_weekends_graph
es_drug_weekends_graph
es_theft_weekends_graph
```

## Weekdays

The following are subsetted from the initial sample above to only include Monday-Thursday. Fixed effects remain the same.

```{r}
es_alc_weekdays_graph
es_sex_weekdays_graph
es_drug_weekdays_graph
es_theft_weekdays_graph
```

## My opinion

When I subset sexual assaults to only weekends, it doesn't seem like there's much of a trend at all. 

## Event studies with alternative fixed effects

Suppose I want to change the fixed effects to a more traditional "two-way" design where I have university fixed effects and semester-number fixed effects. 


