---
title: "Untitled"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(fixest)
library(lubridate)
library(modelsummary)
```

```{r}
source(here::here("Figures/event_study_multiple.R"))
source(here::here("Figures/event_study_weekdays.R"))
source(here::here("Figures/event_study_weekends.R"))
```

# New changes to the model

I decided to change the model a little bit after presenting in reading group. A big fear a lot of people have were that there were lasting effects of a moratorium, which the model does not account for. My previous model assumed that all effects were instantaneous - fraternities stop partying immediately and begin partying immediately following a moratorium and lifting of a moratorium respectively. To combat this, I decided to add in a "week before" and a "week after" control. Each of these controls are indicators equal to 1 for each 7 day period before and following a moratorium. If the effects of this policy is truly instantaneous, I would expect to see dips during treatment, and nulls elsewhere. Results are shown below:


Sexual assault looks to be less convincing of an outcome with these new controls in. It's definitely not as robust as it once was to the different time fixed effects. However, across all models with the university and semester fixed effect, I see significant effects on weekends for alcohol, sexual assault, and drug offenses. With university-by-semester-number fixed effects, I see only significant effects for alcohol. With university and day-by-month-by-year fixed effects, I see significant effects for drug and alcohol offenses. 

## New TWFE literature

One of the challenges of this model is that is does not fit into the TWFE literature exactly. For instance, the new estimators by Callaway and Santanna/Sun and Abram all assume a staggered adoption where once treated, you are treated forever after. Moreover, Goodman-Bacon's bacondecomposition only works for staggered adoptions. Finally, DeChaismartin and De'Houtville's estimator could potentially work for this design, but it requires a balanced panel for their command to work (which my panel is not). The documentation says that it is possible to estimate the model with an unbalanced panel, but there needs to be a lot of tweaking done and contacting the package authors is recommended (which I did but no response). On the bright side, I can do the DeChaismartin/De'Houtville version of the bacondecomposition, although I can only use two models: the model with university and semester fixed effects, or the model with university and day-by-month-by-year fixed effects.

When I use this decomposition I get mixed results. In the date-by-month-by-year fixed effects specification, I get good news: no negative weights so sign reversal is impossible. In the semester-number fixed effects model, I get that the negative weights sum to -.09 while the positive weights sum to 1.09. The package says that this DGP is compatible with one in which there could be sign reversal. 

## What to present

With all this information, it's difficult to figure out what I want to present in the paper as my main findings. 

# Event Studies with preferred specification

Want to produce several event studies. All of these are aggregated up to the weekly level. No further manipulations are used. The time fixed effects are university-by-semester-number.

```{r}
es_alc_graph
es_sex_graph
es_drug_graph
es_theft_graph
```

## Weekends

The following are subsetted from the sample above to only include Friday-Sunday. Fixed effects remain the same.

```{r}
es_alc_weekends_graph
es_sex_weekends_graph
es_drug_weekends_graph
es_theft_weekends_graph
```

## Weekdays

The following are subsetted from the initial sample above to only include Monday-Thursday. Fixed effects remain the same.

```{r}
es_alc_weekdays_graph
es_sex_weekdays_graph
es_drug_weekdays_graph
es_theft_weekdays_graph
```

## My opinion

When I subset sexual assaults to only weekends, it doesn't seem like there's much of a trend at all. Might be worth putting using these as results. 

## Event studies with alternative fixed effects

Suppose I want to change the fixed effects to a more traditional "two-way" design where I have university fixed effects and semester-number fixed effects. 


