---
title: "Referee Notes"
output: pdf_document
date: "2022-10-31"
linkcolor: blue
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{subfig}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# IFC Fraction


## Analysis 1:

The first analysis includes an interaction effect on the preferred specification:

$$Y_{u,t}  = \beta_1InMoratorium_{u,t} + \beta_2InMoratorium_{u,t} \times FracIFC_{u} + 
\gamma_{u} \times AcademicYear_{t} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}$$

\noindent where $FracIFC_{u}$ is the difference of the fraction of IFC members at university $u$ from the mean of all fractions of IFC members at all universities. Hence, this is the Fraction of IFC members at university $u$, but centered at the average across all universities. 


## Analysis 2: Quantiles

The second is interacts indicators for each quartile of the fraction of IFC members with the $InMoratorium_{u,t}$ treatment variable:

$$Y_{u,t}  = \sum_{i=1}^{4}\beta_iInMoratorium_{u,t} \times QuartileIFC_{u,i} + 
\gamma_{u} \times AcademicYear_{t} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}$$


Figure \ref{alc_ifc} shows a possible inverse relationship *on the weekends* between IFC membership and moratorium effects, although the initial point estimate in quartile 1 is much lower than the others. Aside from this point estimate, there appears to be a negative relationship: as IFC membership is higher, the effect of moratoriums is stronger (more negative). The strange blip in the first quartile is caused by West Virginia University. Observe Figure \ref{alc_ifc_2} which shows the the results excluding this university. 

On the other hand, this relationship is much more clear when viewing sexual assaults in Figure \ref{sex_ifc}. Note that I am not exluding any universities here as the relationship looks rather clear.

```{r}
source("referee_analysis/regressions_ifc_fraction.R")
```


\newpage

```{r}
ifc_share
```

```{r, fig.cap="\\label{alc_ifc}The Effect of Moratoriums on Alcohol Offenses by Quartile of IFC Membership"}
alc_ifc
```

```{r, fig.cap="\\label{sex_ifc}The Effect of Moratoriums on Alcohol Offenses by Quartile of IFC Membership"}
sex_ifc
```

