---
title: "Fraction IFC Analysis"
output: pdf_document
linkcolor: blue
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{subfig}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# IFC Fraction

This is analysis that has been redone from the last update I sent you before NYE. The big update here is that I have gathered some more data that I could find based on my FOIA requests for IFC numbers. Hence, the numbers here are more updated. In addition, I also calculated the share more accurately—before I was taking the average IFC share and dividing by the average enrollment. Now, I simply have the average IFC share which is defined as the number of IFC members divided by *undergraduate* enrollment. 

At this point, I don't think there is too much more I can do with this. To me, it looks like the results are just noisey and I can't say much. My hope is that I can throw this into an appendix after discussing it thoroughly in the referee report—but wanted to know your thoughts on this. 

## Analysis 1:

The first analysis includes an interaction effect on the preferred specification:

$$Y_{u,t}  = \beta_1InMoratorium_{u,t} + \beta_2InMoratorium_{u,t} \times FracIFC_{u} + 
\gamma_{u} \times AcademicYear_{t} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}$$

\noindent where $FracIFC_{u}$ is the difference of the fraction of IFC members at university $u$ from the mean of all fractions of IFC members at all universities. Hence, this is the Fraction of IFC members at university $u$, but centered at the average across all universities. The results are shown in Table \ref{ifc_share}.


## Analysis 2: Quartiles

The second analysis interacts indicators for each quartile of the fraction of IFC members with the $InMoratorium_{u,t}$ treatment variable:

$$Y_{u,t}  = \sum_{i=1}^{4}\beta_iInMoratorium_{u,t} \times QuartileIFC_{u,i} + 
\gamma_{u} \times AcademicYear_{t} + \lambda \mathbb{X}_{t} +  \epsilon_{u,t}$$


There does not appear to be much of a relationship between IFC share and moratorium effects as shown in Figures \ref{alc_ifc} and \ref{sex_ifc}. I could keep on splitting them in to different size bins, but at that point it feels as though I am searching for a result to verify a hypothesis.

```{r}
source("referee_analysis/ifc_frac_analysis.R")
```


\newpage

```{r}
ifc_share
```

```{r, fig.cap="\\label{alc_ifc}The Effect of Moratoriums on Alcohol Offenses by Quartile of IFC Membership"}
alc_ifc
```


```{r, fig.cap="\\label{sex_ifc}The Effect of Moratoriums on Sexual Assault Offenses by Quartile of IFC Membership"}
sex_ifc
```

